---
title: "Central Highalnds baseline landis habitat data"
output: html_notebook
author: "GE Ryan"
---

## Prelims

### Packages
```{r packages}
library(raster)
library(sf)
library(dplyr)
library(rgdal)
library(sp)
```
### File paths
```{r paths}
bmpath <- "/home/landis/landis_ch_s1_pb-th-cc/output/biomass/"
cspath <- "/home/landis/landis_ch_s1_pb-th-cc/output/cohort-stats/"
oppath <- "/home/landis/landis_steps/output/"
```

## Landscape
```{r ch_rst}
ch_rst <- raster("~/landis_steps/data/grids/landis/eco_v12.img")
```

Gather spatial information from base layer:
```{r }
ch_res <- res(ch_rst)
ch_extent <- extent(ch_rst)
ch_proj <- ch_rst@crs
```

Create 1km2 window for focal operations:
```{r}
buffer_radius <- 564
window <- focalWeight(raster(ncols=11, nrows=11, xmn = 0, resolution = 100),
                      buffer_radius,
                      type = 'circle')
```

Load in Central Highlands boundary and rasterize as a mask
```{r}
rfa_boundary <- readOGR(dsn="~/landis_steps/data/shapefiles", layer="RFA")
rfa_boundary <- rfa_boundary[rfa_boundary@data$NAME == "CENTRAL HIGHLANDS", ]
rfa_boundary <- spTransform(rfa_boundary, ch_proj)

ch_mask <- rasterize(rfa_boundary, ch_rst, field = 1)
#writeRaster(ch_mask, file = "~/landis_steps/data/grids/ch_mask.tif", overwrite = TRUE)
```

```{r}
rfa_boundary <- re
```



```{r}
vic <- read_sf(dsn = "/home/landis/landis_steps/data/shapefiles/vicstatepolygon/", layer = "VIC_STATE_POLYGON_shp") %>%
  st_transform(crs = 32755)

vic
```


```{r}
plot(ch_mask)
```

## Process Landis Data

### Initial year

#### Biomass
This creates a raster for year 0 for biomass of each species named in the 8 letter 4-4 genus-species format from landis
```{r biomass}
spp <- list.files(path = bmpath,
                  pattern = "bio-") %>%
  sub("bio-", "", .) %>%
  sub("-.*", "", .) %>%
  unique

spp

for(i in 1:length(spp)){
  
  tempraster <- ch_mask
  
  tempraster[] <- sprintf("%sbio-%s-0.img", bmpath, spp[i]) %>%
    raster %>%
    getValues
  
  names(tempraster) <- spp[i]
  
  assign(sprintf("biomass_%s", spp[i]), tempraster)
  
}
```


**need to up update species list in next run**
```{r}
spp <- list.files(path = cspath,
                  ) %>%
  sub("-.*", "", .) %>%
  unique

spp <- spp[which(spp!= "AGE")]
spp <- spp[which(spp!= "SPP")]

for(i in 1:length(spp)){
  
  tempraster <- ch_mask
  
  tempraster[] <- sprintf("%s%s-MAX-0.img", cspath, spp[i]) %>%
    raster %>%
    getValues
  
  names(tempraster) <- spp[i]
  
  assign(sprintf("maxage_%s", spp[i]), tempraster)
  
}
```


#### Max age
```{r max age}
max_age <- ch_mask

max_age[] <- paste0(cspath, "AGE-MAX-0.img") %>%
  raster %>%
  getValues
```

#### Indices

##### CV GG Model
```{r max age 150 & 200}
max_age_150 <- max_age
max_age_150[max_age_150 < 150] <- 0
max_age_150[max_age_150 != 0] <- 1

max_age_200 <- max_age
max_age_200[max_age_200 < 200] <- 0
max_age_200[max_age_200 != 0] <- 1

prop_old_150 <- focal(max_age_150, window, na.rm = TRUE)
prop_old_200 <- focal(max_age_200, window, na.rm = TRUE)

#writeRaster(prop_old_150, file = paste0(oppath, "prop_old_150_00.tif"), overwrite = TRUE)
#writeRaster(prop_old_200, file = paste0(oppath, "prop_old_200_00.tif"), overwrite = TRUE)
```
?? Window buffer size appropriate?

```{r cv eucs}
biomass_eucs <- biomass_eucs <- stack(biomass_eucacype, biomass_eucadalr, biomass_eucadive, biomass_eucaradi, biomass_eucavimi)

biomass_eucs_mat <- getValues(biomass_eucs)

biomass_TotalBiomass_vec <- getValues(biomass_TotalBiomass)

prop_bio_targ <- ch_mask
prop_bio_targ[] <- rowSums(biomass_eucs_mat)/biomass_TotalBiomass_vec

prop_bio_regn <- ch_mask
prop_bio_regn[] <- getValues(biomass_eucaregn)/biomass_TotalBiomass_vec

#writeRaster(prop_bio_targ, file = paste0(oppath, "prop_bio_targ_00.tif"), overwrite = TRUE)
#writeRaster(prop_bio_regn, file = paste0(oppath, "prop_bio_regn_00.tif"), overwrite = TRUE)
```


##### HBT
```{r}
hbt <- ch_mask

hbt[] <- getValues(max_age)
hbt[hbt <= 150] <- 0
hbt[hbt > 150 & hbt < 200] <- (hbt[hbt > 150 & hbt < 200] - 150)/50
hbt[hbt >= 200] <- 1

plot(hbt)
```


##### GG denning
```{r}
ggdspp <- stack(biomass_eucacype, biomass_eucadalr, biomass_eucadive, biomass_eucaradi, biomass_eucaregn, biomass_eucavimi)

ggdspp_mat <- getValues(ggdspp)
ggdspp_vec <- rowSums(ggdspp_mat)

ggdspp <- ch_mask

ggdspp[] <- ggdspp_vec

ggdspp[ggdspp > 0] <- 1
```

```{r}
plot(ggdspp)
```


##### GG foraging
window this?
```{r}
ggfspp <- stack(biomass_eucacype, biomass_eucaglob, biomass_eucaobli, biomass_eucatric)

ggfspp_mat <- getValues(ggfspp)
ggfspp_vec <- rowSums(ggfspp_mat)

ggfspp <- ch_mask

ggfspp[] <- ggfspp_vec

ggfspp[ggfspp > 0] <- 1
```


```{r}
plot(ggfspp)
```
##### LBP mid-storey
probably need eucaacer in future runs

stupid because means of these things isn't very useful - great habitat in one of these is all that's needed
```{r}
lbdspp <- stack(biomass_acacdeal, biomass_acacmear, biomass_acacobli, biomass_eucadeli, biomass_eucanite, biomass_eucapauh, biomass_eucapaul, biomass_eucaregn, biomass_leptgran, biomass_nothcunn)

lbdspp_mat <- getValues(lbdspp)
lbdspp_mat[lbdspp_mat > 0] <- 1
lbdspp_vec <- rowMeans(lbdspp_mat)

lbdspp <- ch_mask

lbdspp[] <- lbdspp_vec
```

use cumulative or propn biomass instead of index
```{r}
lbmspp <- stack(biomass_acacdeal, biomass_acacmear, biomass_acacobli, biomass_eucapauh, biomass_eucapaul, biomass_leptgran, biomass_nothcunn) # is nothofagus appropriate here? do we differentiate mid storey foraging habitat vs stuff they eat?

lbmspp_mat <- getValues(lbmspp)
lbmspp_mat[lbmspp_mat > 0] <- 1
lbmspp_vec <- rowSums(lbmspp_mat)
lbmspp_vec[lbmspp_vec > 0] <-1

lbm <- ch_mask

lbm[] <- lbmspp_vec
```


```{r}
plot(lbm)
```

#### lbphbt
```{r}
buffer_radius_3h <- 100
window_3h <- focalWeight(raster(ncols=3, nrows=3, xmn = 0, resolution = 100),
                      buffer_radius_3h,
                      type = 'rectangle')
window_3h[] <- 1

lbhspp <- stack(maxage_eucaregn, maxage_eucadeli, maxage_eucanite, maxage_eucapauh, maxage_eucapaul)

lbhspp_mat <- getValues(lbhspp)
lbhspp_mat[lbhspp_mat > 0] <- 1
lbhspp_vec <- rowSums(lbhspp_mat)
lbhspp_vec[lbhspp_vec > 0] <- 1

lbh <- ch_mask

lbh[] <- lbhspp_vec

lbhf <- focal(lbh, window_3h, na.rm = TRUE)
lbhf[lbhf < 1.5] <- 0
lbhf[lbhf > 0 ] <- 0.4*lbhf[lbhf > 0] -0.6
lbhf[lbhf > 1] <- 1
```

```{r}
plot(lbhf)
```

## Climate vars
```{r}
prec01 <- raster("~/landis_steps/data/grids/bioclim/wc2.0_30s_prec_01.tif")
prec01 <- projectRaster(prec01, ch_mask)
prec01 <- mask(prec01, ch_mask)

plot(prec01)
```

```{r}
prec07 <- raster("~/landis_steps/data/grids/bioclim/wc2.0_30s_prec_07.tif")
prec07 <- projectRaster(prec07, ch_mask)
prec07 <- mask(prec07, ch_mask)

plot(prec07)
```

```{r}
tmax01 <- raster("~/landis_steps/data/grids/bioclim/wc2.0_30s_tmax_01.tif")
tmax01 <- projectRaster(tmax01, ch_mask)
tmax01 <- mask(tmax01, ch_mask)

plot(tmax01)
```

```{r}
tmin07 <- raster("~/landis_steps/data/grids/bioclim/wc2.0_30s_tmin_07.tif")
tmin07 <- projectRaster(tmin07, ch_mask)
tmin07 <- mask(tmin07, ch_mask)

plot(tmin07)
```

```{r}
ggplot() + geom_raster(data = as.data.frame(tmin07, xy = T), aes(x = x, y = y, fill = wc2.0_30s_tmin_07)) + scale_fill_viridis_c()
```

## collate vars
```{r}
#gg_init_env_vars <- stack(prec01, prec07, tmax01, tmin07, prop_bio_regn, prop_bio_targ, prop_old_150, prop_old_200)

#names(gg_init_env_vars) <- c("prec01", "prec07", "tmax01", "tmin07", "prop_bio_regn", "prop_bio_targ", "prop_old_150", "prop_old_200")

gg_init_env_vars <- stack(prop_bio_regn, prop_bio_targ, prop_old_150, prop_old_200)

names(gg_init_env_vars) <- c("prop_bio_regn", "prop_bio_targ", "prop_old_150", "prop_old_200")


save(gg_init_env_vars, file = "/home/landis/landis_steps/data/gg_init_env_vars")
```

```{r}
lb_init_env_vars <- stack(prec01, prec07, tmax01, tmin07, lbhf, lbm)

names(lb_init_env_vars) <- c("prec01", "prec07", "tmax01", "tmin07", "lbhf", "lbm")

save(lb_init_env_vars, file = "/home/landis/landis_steps/data/lb_init_env_vars")
```


## points
```{r}
gg_pres_abs <- read.csv(file="/home/landis/landis_steps/data/tabular/vba_greater_glider_2009-2019_PA.csv")
table(gg_pres_abs$PA)

gg_pres_abs <- SpatialPointsDataFrame(coords = cbind("X" = gg_pres_abs$LongitudeGDA94, "Y" = gg_pres_abs$LatitudeGDA94),
                                      data = data.frame("PA" = gg_pres_abs$PA),
                                      proj4string = CRS("+proj=longlat +datum=WGS84"))

gg_pres_abs <- spTransform(gg_pres_abs, ch_proj)

#gg_pres_abs <- gg_pres_abs[rfa_boundary, ]

table(gg_pres_abs$PA)

plot(gg_pres_abs, col=c("darkred", "darkblue"), pch=c(4,20), cex=c(0.5,0.8))
plot(rfa_boundary, add = TRUE)

#writeOGR(gg_pres_abs, dsn = "/home/landis/landis_steps/data/shapefiles", layer = "gg_points", driver = "ESRI Shapefile", overwrite_layer = TRUE)

#gg_points <- data.frame(gg_pres_abs@data, gg_pres_abs@coords)
```

```{r}
gg_pres_abs <- read.csv(file="/home/landis/landis_steps/data/tabular/vba_greater_glider_2009-2019_PA.csv")
table(gg_pres_abs$PA)

gg_pres_abs <- SpatialPointsDataFrame(coords = cbind("X" = gg_pres_abs$LongitudeGDA94, "Y" = gg_pres_abs$LatitudeGDA94),
                                      data = data.frame("PA" = gg_pres_abs$PA),
                                      proj4string = CRS("+proj=longlat +datum=WGS84"))

gg_pres_abs <- st_as_sf(gg_pres_abs, coords = c("LongitudeGDA94", "LatitudeGDA94"), crs = 4326)

bo <- st_read()

st_transform()

st_crs(32755)

gg_pres_abs <- spTransform(gg_pres_abs, ch_proj)

plot(rfa_boundary)
plot(gg_pres_abs, add = TRUE, col = gg_pres_abs$PA)

library(ggplot2)
ggplot() +
  geom_sf(data = vic) +
  geom_sf(data = st_as_sf(rfa_boundary)) +
  geom_sf(data = st_as_sf(gg_pres_abs), aes(color = as.factor(PA)), size = 0.1) +
  theme_bw()

gg_pres_abs <- gg_pres_abs[rfa_boundary, ]
gg_pres_abs$PA

table(gg_pres_abs$PA)

plot(gg_pres_abs, col=c("darkred", "darkblue"), pch=c(4,20), cex=c(0.5,0.8))
plot(rfa_boundary, add = TRUE)
```


```{r}
lb_pres_abs <- read.csv(file="/home/landis/landis_steps/data/tabular/vba_lbp_2009-2019_PA.csv")

lb_pres_abs <- SpatialPointsDataFrame(coords = cbind("X" = lb_pres_abs$LongitudeGDA94, "Y" = lb_pres_abs$LatitudeGDA94),
                                      data = data.frame("PA" = lb_pres_abs$PA),
                                      proj4string = CRS("+proj=longlat +datum=WGS84"))

lb_pres_abs <- spTransform(lb_pres_abs, ch_proj)
lb_pres_abs <- lb_pres_abs[rfa_boundary, ]

plot(lb_pres_abs, col=c("darkred", "darkblue"), pch=c(4,20), cex=c(0.5,0.8))

writeOGR(lb_pres_abs, dsn = "/home/landis/landis_steps/data/shapefiles", layer = "lb_points", driver = "ESRI Shapefile", overwrite_layer = TRUE) ## can change over to st_write

lb_points <- data.frame(lb_pres_abs@data, lb_pres_abs@coords)

table(lb_points$PA)
```



### Sample data

```{r}
load(file="/home/landis/landis_steps/data/gg_init_env_vars")

# Sample covariate values
cov_sample <- as.data.frame(extract(gg_init_env_vars, gg_points[, 2:3]))

# Create modelling dataset
gg_model_data <- cbind("PA" = gg_points[, 1], cov_sample)
```

```{r}
load(file="/home/landis/landis_steps/data/lb_init_env_vars")

# Sample covariate values
cov_sample <- as.data.frame(extract(lb_init_env_vars, lb_points[, 2:3]))

# Create modelling dataset
lb_model_data <- cbind("PA" = lb_points[, 1], cov_sample)
```



```{r}
# Check for NA values and omit accordingly:
sum(is.na(gg_model_data))
gg_model_data <- na.omit(gg_model_data)
```


```{r}
#cor(gg_model_data[, 2:9])
cor(gg_model_data[, 2:5])
```

 Review covariate data types
```{r}
str(gg_model_data)
```
Review data ranges
```{r}
#apply(gg_model_data[, 2:9], 2, range)
apply(gg_model_data[, 2:5], 2, range)
```
Split the data into training and testing data
```{r}
set.seed(123)
gg_sample <- sample(nrow(gg_model_data), round(0.75 * nrow(gg_model_data))) # the row indexes of our 75% sample
gg_model_data_75 <- gg_model_data[gg_sample, ] # 75% of the data used to train the model
gg_model_data_25 <- gg_model_data[-gg_sample, ] # 25% of the data used to test the model
```

Write the modelling data out to csv files and as an R object
```{r}
write.csv(gg_model_data, file = "/home/landis/landis_steps/data/gg_model_data.csv")
write.csv(gg_model_data_25, file = "/home/landis/landis_steps/data/gg_model_data_25.csv")
write.csv(gg_model_data_75, file = "/home/landis/landis_steps/data/gg_model_data_75.csv")
save("gg_model_data", "gg_model_data_25", "gg_model_data_75", file = "/home/landis/landis_steps/data/gg_model_datasets")
```


```{r}
# Check for NA values and omit accordingly:
sum(is.na(lb_model_data))
lb_model_data <- na.omit(lb_model_data)
```


```{r}
cor(lb_model_data[, 2:7])
```

 Review covariate data types
```{r}
str(lb_model_data)
```
Review data ranges
```{r}
apply(lb_model_data[, 2:7], 2, range)
```
Split the data into training and testing data
```{r}
set.seed(123)
lb_sample <- sample(nrow(lb_model_data), round(0.75 * nrow(lb_model_data))) # the row indexes of our 75% sample
lb_model_data_75 <- lb_model_data[lb_sample, ] # 75% of the data used to train the model
lb_model_data_25 <- lb_model_data[-lb_sample, ] # 25% of the data used to test the model
```

Write the modelling data out to csv files and as an R object
```{r}
write.csv(lb_model_data, file = "/home/landis/landis_steps/data/lb_model_data.csv")
write.csv(lb_model_data_25, file = "/home/landis/landis_steps/data/lb_model_data_25.csv")
write.csv(lb_model_data_75, file = "/home/landis/landis_steps/data/lb_model_data_75.csv")
save("lb_model_data", "lb_model_data_25", "lb_model_data_75", file = "/home/landis/landis_steps/data/lb_model_datasets")
```


## Fire
```{r}
fihi <- read_sf("/home/landis/landis_steps/data/shapefiles/vicfires/")
```

```{r}
plot(fihi)
```

```{r}
fhr <- raster(fihi, band = SEASON) ## doesn't work
```


### Future years