---
title: "Habitat Model Data Landis"
author: "Casey Visintin"
date: "26 February 2019"
output: html_document
---

```{r setup, include = FALSE, cache = FALSE}
library(raster)
library(rgdal)
library(rgeos)
library(dismo)
library(viridis)
library(foreach)
library(doMC)
#library(doParallel)
library(maptools)
library(sf)
knitr::opts_chunk$set(echo = TRUE)
path <- "/home/landis/landis_ch_s1_pb-th-cc/output/biomass/"
source("R/functions/rascc.R")
```

Load a spatial layer from LANDIS as a base layer:

```{r}
ch_rst <- raster("data/grids/landis/eco_v12.img")
```

Gather spatial information from base layer:

```{r}
ch_res <- res(ch_rst)
ch_extent <- extent(ch_rst)
ch_proj <- ch_rst@crs
```

Create 1km2 window for focal operations:

```{r}
buffer_radius <- 564
window <- focalWeight(raster(ncols=11, nrows=11, xmn = 0, resolution = 100),
                      buffer_radius,
                      type = 'circle')
```

Load in Central Highlands boundary and rasterize as a mask

```{r}
rfa_boundary <- readOGR(dsn="data/shapefiles", layer="RFA")
rfa_boundary <- rfa_boundary[rfa_boundary@data$NAME == "CENTRAL HIGHLANDS", ]
rfa_boundary <- spTransform(rfa_boundary, ch_proj)

ch_mask <- rasterize(rfa_boundary, ch_rst, field = 1)
writeRaster(ch_mask, file = paste0(path, "../../ch_mask.tif"), overwrite = TRUE)
```

```{r}
plot(ch_mask)
```

```{r}
plot(rfa_boundary)
```




Process raw LANDIS spatial data - this involves copying raster values into new rasters based on project standards.

Variables available - Maximum Age of each of the six target species and total, Total Biomass of each species and total, Total Species Richness, Total dead biomass.


# Euc vars

```{r}
path <- "/home/landis/landis_ch_s1_pb-th-cc/output/biomass/"
biomass_tot <- ch_mask
biomass_tot[] <- getValues(raster(paste0(path, "bio-TotalBiomass-0.img")))
biomass_tot <- biomass_tot * ch_mask

biomass_tot_vec <- getValues(biomass_tot)

biomass_eucacype <- biomass_eucadalr <- biomass_eucadive <- biomass_eucaradi <- biomass_eucaregn <- biomass_eucavimi <- ch_rst

biomass_eucacype[] <- getValues(raster(paste0(path, "bio-eucacype-0.img")))
biomass_eucadalr[] <- getValues(raster(paste0(path, "bio-eucadalr-0.img")))
biomass_eucadive[] <- getValues(raster(paste0(path, "bio-eucadive-0.img")))
biomass_eucaradi[] <- getValues(raster(paste0(path, "bio-eucaradi-0.img")))
biomass_eucaregn[] <- getValues(raster(paste0(path, "bio-eucaregn-0.img")))
biomass_eucavimi[] <- getValues(raster(paste0(path, "bio-eucavimi-0.img")))

biomass_eucs <- stack(biomass_eucacype, biomass_eucadalr, biomass_eucadive, biomass_eucaradi, biomass_eucavimi)
#biomass_eucs <- stack(biomass_eucacype, biomass_eucadalr, biomass_eucaradi, biomass_eucaregn, biomass_eucavimi)

biomass_eucs <- biomass_eucs * ch_mask


names(biomass_eucs) <- unique(gsub("-{1}.{1,2}\\.img", "",
                                    list.files(path, pattern = "bio-euca")))[c(2, 3,6, 12, 15)]


biomass_eucs_mat <- getValues(biomass_eucs)
```

```{r}
path <- "/home/landis/landis_ch_s1_pb-th-cc/output/biomass/"

biomass_acacdeal <- ch_rst

biomass_acacdeal[] <- getValues(raster(paste0(path, "bio-acacdeal-0.img")))
biomass_acacdeal <- biomass_acacdeal * ch_mask
```


```{r}
path <- "/home/landis/landis_ch_s1_pb-th-cc/output/cohort-stats/"
max_age_200 <- ch_rst
max_age_200[] <- getValues(raster(paste0(path, "AGE-MAX-0.img")))
max_age_200[max_age_200 < 200] <- 0
max_age_200[max_age_200 != 0] <- 1
max_age_200 <- max_age_200 * ch_mask

max_age_150 <- ch_rst
max_age_150[] <- getValues(raster(paste0(path, "AGE-MAX-0.img")))
max_age_150[max_age_150 < 150] <- 0
max_age_150[max_age_150 != 0] <- 1
max_age_150 <- max_age_150 * ch_mask
```


```{r}
hbt <- ch_rst
path <- "/home/landis/landis_ch_s1_pb-th-cc/output/cohort-stats/"

hbt[] <- getValues(raster(paste0(path, "AGE-MAX-0.img")))
hbt[hbt <= 150] <- 0
hbt[hbt > 150 & hbt < 200] <- (hbt[hbt > 150 & hbt < 200] - 150)/50
hbt[hbt >= 200] <- 1
```

Create new spatial inputs based on LANDIS outputs:

PROP_BIO_TARG <- Proportion of total biomass for all five target species (eucacype, eucadalr, eucadive, eucaradi, eucavimi) combined
PROP_BIO_REGN <- Proportion of total biomass for regnans species
PROP_OLD_200 <- Total proportion of old (>200 years) trees within 1km2
PROP_OLD_150 <- Total proportion of old (>200 years) trees within 1km2

```{r}
path <- "data/grids"
PROP_BIO_TARG <- ch_rst
PROP_BIO_TARG[] <- rowSums(biomass_eucs_mat) / biomass_tot_vec
writeRaster(PROP_BIO_TARG, file = paste0(path, "/output/PROP_BIO_TARG-00.tif"), overwrite = TRUE)

PROP_BIO_REGN <- ch_rst
PROP_BIO_REGN[] <- getValues(biomass_eucaregn) / biomass_tot_vec
writeRaster(PROP_BIO_REGN, file = paste0(path, "/output/PROP_BIO_REGN-00.tif"), overwrite = TRUE)

PROP_OLD_200 <- focal(max_age_200, window, na.rm = TRUE)
writeRaster(PROP_OLD_200, file = paste0(path, "/output/PROP_OLD_200-00.tif"), overwrite = TRUE)

PROP_OLD_150 <- focal(max_age_150, window, na.rm = TRUE)
writeRaster(PROP_OLD_150, file = paste0(path, "/output/PROP_OLD_150-00.tif"), overwrite = TRUE)

PROP_HBT
```

Combine all spatial data to produce modelling variable stack:

```{r}
gg_init_env_vars <- stack(PROP_BIO_TARG, PROP_BIO_REGN, PROP_OLD_200, PROP_OLD_150)
names(gg_init_env_vars) <- c("PROP_BIO_TARG", "PROP_BIO_REGN", "PROP_OLD_200", "PROP_OLD_150")

save(gg_init_env_vars, file="data/gg_init_env_vars")
```


```{r}
read
lbp_init_env_vars <- stack(PROP_BIO_TARG, PROP_BIO_REGN, PROP_OLD_200, PROP_OLD_150, biomass_acacdeal)
names(gg_init_env_vars) <- c("PROP_BIO_TARG", "PROP_BIO_REGN", "PROP_OLD_200", "PROP_OLD_150", "biomass_acacdeal")

save(lbp_init_env_vars, file="data/lbp_init_env_vars")
```

Load in Greater Glider presence and absence data and reproject:

```{r}
gg_pres_abs <- read.csv(file="data/tabular/vicAtlasGGpresabs.csv")

gg_pres_abs <- SpatialPointsDataFrame(coords = cbind("X" = gg_pres_abs$LongitudeGDA94, "Y" = gg_pres_abs$LatitudeGDA94),
                                      data = data.frame("PA" = gg_pres_abs$PA),
                                      proj4string = CRS("+init=epsg:4283"))

gg_pres_abs <- spTransform(gg_pres_abs, ch_proj)
gg_pres_abs <- gg_pres_abs[rfa_boundary, ]

plot(gg_pres_abs, col=c("darkred", "darkblue"), pch=c(4,20), cex=c(0.5,0.8))

writeOGR(gg_pres_abs, dsn = "data/shapefiles", layer = "gg_points", driver = "ESRI Shapefile", overwrite_layer = TRUE)

GG_POINTS <- data.frame(gg_pres_abs@data, gg_pres_abs@coords)

# GG_POINTS <- data.frame(
#   rbind(
#     cbind("PA" = 1, gridSample(xy = gg_pres_abs[gg_pres_abs@data$PA == 1,],
#                         r = ch_rst,
#                         n = 1)),
#     cbind("PA" = 0, gridSample(xy = gg_pres_abs[gg_pres_abs@data$PA == 0,],
#                         r = ch_rst,
#                         n = 1))))

```

Verify spatial attributes representing potential autocorrelation:

```{r}
gg_points_sf <- st_as_sf(data.frame(GG_POINTS[, 2:3]), coords = c("X", "Y"), crs = 28355)
gg_points_sf_pres <- st_as_sf(data.frame(GG_POINTS[GG_POINTS$PA == 1, 2:3]), coords = c("X", "Y"), crs = 28355)
gg_points_sf_abs <- st_as_sf(data.frame(GG_POINTS[GG_POINTS$PA == 0, 2:3]), coords = c("X", "Y"), crs = 28355)

dists_all <- st_distance(gg_points_sf, gg_points_sf)
dists_all <- apply(dists_all, 1, function(x) min(x[x != 0]))
plot(density(dists_all))

dists_pres <- st_distance(gg_points_sf_pres, gg_points_sf_pres)
dists_pres <- apply(dists_pres, 1, function(x) min(x[x != 0]))
plot(density(dists_pres))

dists_abs <- st_distance(gg_points_sf_abs, gg_points_sf_abs)
dists_abs <- apply(dists_abs, 1, function(x) min(x[x != 0]))
plot(density(dists_abs))
```

Sample predictor maps with Greater Glider presence and absence points and create modelling dataset:

```{r}
load(file="data/gg_init_env_vars")

# Sample covariate values
cov_sample <- as.data.frame(extract(gg_init_env_vars, GG_POINTS[, 2:3]))

# Create modelling dataset
gg_model_data <- cbind("PA" = GG_POINTS[, 1], cov_sample)

```

Import and process roads data to construct bias information:
*not run*
```{r}
# roads <- st_read("data/shapefiles/VIC_GDA9455_ROADS_STATE.shp")
# roads <- st_crop(roads, extent(ch_extent))
# roads_simp <- st_union(roads)
# save(roads_simp, file="data/roads_simp")
# st_write(roads_simp, dsn = "data/shapefiles/roads_simplified.shp", driver = "ESRI Shapefile", delete_layer = TRUE)

load(file="data/roads_simp")

gg_points_sf <- st_as_sf(data.frame(GG_POINTS[, 2:3]), coords = c("X", "Y"), crs = 28355)

bias_sample <- st_distance(gg_points_sf, roads_simp)

# Append to modelling dataset
gg_model_data <- cbind(gg_model_data, "DIST_ROADS" = as.vector(bias_sample))

```

Inspect data and create modelling training and testing datasets:

```{r}
# Check for NA values and omit accordingly:
sum(is.na(gg_model_data))
gg_model_data <- na.omit(gg_model_data)

# Review pairwise correlation of covariates:
#cor(gg_model_data[, 2:6])
cor(gg_model_data[, 2:5])#no roads

# Review covariate data types
str(gg_model_data)

# Review data ranges
#apply(gg_model_data[, 2:6], 2, range)
apply(gg_model_data[, 2:5], 2, range)

# Split the data into training and testing data
set.seed(123)
gg_sample <- sample(nrow(gg_model_data), round(0.75 * nrow(gg_model_data))) # the row indexes of our 75% sample
gg_model_data_75 <- gg_model_data[gg_sample, ] # 75% of the data used to train the model
gg_model_data_25 <- gg_model_data[-gg_sample, ] # 25% of the data used to test the model

# Write the modelling data out to csv files and as an R object
write.csv(gg_model_data, file = "data/gg_model_data.csv")
write.csv(gg_model_data_25, file = "data/gg_model_data_25.csv")
write.csv(gg_model_data_75, file = "data/gg_model_data_75.csv")
save("gg_model_data", "gg_model_data_25", "gg_model_data_75", file = "data/gg_model_datasets")
```

Create predictor maps for all future timesteps:

```{r, progress = FALSE}
path <- "/home/landis/landis_ch_lbp/output/biomass/"

#eucs_names <- unique(gsub("-{1}.{1,2}\\.img", "",
#                                    list.files(path, pattern = "bio-euca")))[-5]

eucs_names <- unique(gsub("-{1}.{1,2}\\.img", "",
                                    list.files(path, pattern = "bio-euca")))[c(2, 3, 9, 10, 11)]

#DIST_ROADS <- ch_mask
#DIST_ROADS[DIST_ROADS == 1] <- 0
#names(DIST_ROADS) <- "DIST_ROADS"

timesteps <- 50

#cl <- makePSOCKcluster(20)

#registerDoParallel(cl = cl)
timestamp()
registerDoMC(cores = 20)

gg_fut_env_vars <- foreach (i = seq_len(timesteps)) %dopar% {
  
  path <- "/home/landis/landis_ch_lbp/output/biomass/"
  biomass_tot <- ch_mask
  biomass_tot[] <- getValues(raster(paste0(path, "bio-TotalBiomass-",i ,".img")))
  biomass_tot <- biomass_tot * ch_mask
  biomass_tot_vec <- getValues(biomass_tot)

  biomass_eucacype <- biomass_eucadalr <- biomass_eucadive <- biomass_eucaradi <- biomass_eucaregn <- biomass_eucavimi <- ch_rst

  biomass_eucacype[] <- getValues(raster(paste0(path, "bio-eucacype-",i, ".img")))
  biomass_eucadalr[] <- getValues(raster(paste0(path, "bio-eucadalr-",i, ".img")))
  biomass_eucadive[] <- getValues(raster(paste0(path, "bio-eucadive-",i, ".img")))
  biomass_eucaradi[] <- getValues(raster(paste0(path, "bio-eucaradi-",i, ".img")))
  biomass_eucaregn[] <- getValues(raster(paste0(path, "bio-eucaregn-",i, ".img")))
  biomass_eucavimi[] <- getValues(raster(paste0(path, "bio-eucavimi-",i, ".img")))

  #biomass_eucs <- stack(biomass_eucacype, biomass_eucadalr, biomass_eucadive, biomass_eucaradi, biomass_eucavimi)
  biomass_eucs <- stack(biomass_eucacype, biomass_eucadalr, biomass_eucaradi, biomass_eucaregn, biomass_eucavimi)

  biomass_eucs <- biomass_eucs * ch_mask

  names(biomass_eucs) <- eucs_names

  biomass_eucs_mat <- getValues(biomass_eucs)

  
  path <- "/home/landis/landis_ch_lbp/output/cohort-stats/"
  
  max_age_200 <- ch_rst
  max_age_200[] <- getValues(raster(paste0(path, "AGE-MAX-",i, ".img")))
  max_age_200[max_age_200 < 200] <- 0
  max_age_200[max_age_200 != 0] <- 1
  max_age_200 <- max_age_200 * ch_mask

  max_age_150 <- ch_rst
  max_age_150[] <- getValues(raster(paste0(path, "AGE-MAX-",i, ".img")))
  max_age_150[max_age_150 < 150] <- 0
  max_age_150[max_age_150 != 0] <- 1
  max_age_150 <- max_age_150 * ch_mask
  
  PROP_BIO_TARG <- ch_rst
  PROP_BIO_TARG[] <- rowSums(biomass_eucs_mat) / biomass_tot_vec

  PROP_BIO_REGN <- ch_rst
  PROP_BIO_REGN[] <- getValues(biomass_eucaregn) / biomass_tot_vec

  PROP_OLD_200 <- focal(max_age_200, window, na.rm = TRUE)

  PROP_OLD_150 <- focal(max_age_150, window, na.rm = TRUE)

  stack(PROP_BIO_TARG, PROP_BIO_REGN, PROP_OLD_200, PROP_OLD_150)
}

timestamp()
#stopCluster(cl)


gg_fut_env_vars <- lapply(gg_fut_env_vars, function (x) {
  names(x) <- c("PROP_BIO_TARG", "PROP_BIO_REGN", "PROP_OLD_200", "PROP_OLD_150")
  x})

save(gg_fut_env_vars, file="data/gg_fut_env_vars")
```


