---
title: "Bioclim variables"
author: "GE Ryan"
output: html_notebook
---

## Prelims

### Packages
```{r}
library(tidyr)
library(dplyr)
library(raster)
```

### Functions
```{r}
source(file = "R/functions/rascc.R")
source(file = "R/functions/read.multi.line.header.R")
```

### Mask
```{r}
proj_mask <- raster(x = "~/landis_steps/")
proj_mask <- raster(x = "~/landis_steps/data/grids/ch_mask.tif")
```

## Future Climate Data
Data from [Climate Change in Australia](https://www.climatechangeinaustralia.gov.au/en/)
pc ~ percentage change
ac ~ absolute change

tmax ~ max temperature
tmin ~ minimum temperature
rain ~ precipitation
evtr ~ evapotranspiration

jan ~ January
jul ~ July

4.5 ~ rcp 4.5
8.5 ~ rcp 8.5

Absolute change in temperature
```{r}
#absolute change in temp
raw_tmax_jan_4.5_ac <- read.multi.line.header(file = "http://nrm-erddap.nci.org.au/erddap/griddap/tasmax_Amon_CSIRO-Mk3-6-0_rcp45_r1i1p1_abs-change-wrt-seasavg-clim_native.csv?tasmax_january[(2025-01-01T12:00:00Z):1:(2090-01-01T12:00:00Z)][(-40.10297775):1:(-32.64199448)][(140.625):1:(150)]")

raw_tmax_jan_8.5_ac <- read.multi.line.header(file = "http://nrm-erddap.nci.org.au/erddap/griddap/tasmax_Amon_CSIRO-Mk3-6-0_rcp85_r1i1p1_abs-change-wrt-seasavg-clim_native.csv?tasmax_january[(2025-01-01T12:00:00Z):1:(2090-01-01T12:00:00Z)][(-40.10297775):1:(-32.64199448)][(140.625):1:(150)]")

raw_tmin_jul_4.5_ac <- read.multi.line.header(file = "http://nrm-erddap.nci.org.au/erddap/griddap/tasmin_Amon_CSIRO-Mk3-6-0_rcp45_r1i1p1_abs-change-wrt-seasavg-clim_native.csv?tasmin_july[(2025-01-01T12:00:00Z):1:(2090-01-01T12:00:00Z)][(-40.10297775):1:(-32.64199448)][(140.625):1:(150)]") 

raw_tmin_jul_8.5_ac <- read.multi.line.header(file = "http://nrm-erddap.nci.org.au/erddap/griddap/tasmin_Amon_CSIRO-Mk3-6-0_rcp85_r1i1p1_abs-change-wrt-seasavg-clim_native.csv?tasmin_july[(2025-01-01T12:00:00Z):1:(2090-01-01T12:00:00Z)][(-40.10297775):1:(-32.64199448)][(140.625):1:(150)]")
```

Percentage change in rainfall
```{r}
raw_rain_jan_4.5_pc <- read.multi.line.header(file = "http://nrm-erddap.nci.org.au/erddap/griddap/pr_Amon_CSIRO-Mk3-6-0_rcp45_r1i1p1_perc-change-wrt-seassum-clim_native.csv?pr_january[(2025-01-01T12:00:00Z):1:(2090-01-01T12:00:00Z)][(-40.10297775):1:(-32.64199448)][(140.625):1:(150)]")

raw_rain_jan_8.5_pc <- read.multi.line.header(file = "http://nrm-erddap.nci.org.au/erddap/griddap/pr_Amon_CSIRO-Mk3-6-0_rcp85_r1i1p1_perc-change-wrt-seassum-clim_native.csv?pr_january[(2025-01-01T12:00:00Z):1:(2090-01-01T12:00:00Z)][(-40.10297775):1:(-32.64199448)][(140.625):1:(150)]")

raw_rain_jul_4.5_pc <- read.multi.line.header(file = "http://nrm-erddap.nci.org.au/erddap/griddap/pr_Amon_CSIRO-Mk3-6-0_rcp45_r1i1p1_perc-change-wrt-seassum-clim_native.csv?pr_july[(2025-01-01T12:00:00Z):1:(2090-01-01T12:00:00Z)][(-40.10297775):1:(-32.64199448)][(140.625):1:(150)]")

raw_rain_jul_8.5_pc <- read.multi.line.header(file = "http://nrm-erddap.nci.org.au/erddap/griddap/pr_Amon_CSIRO-Mk3-6-0_rcp85_r1i1p1_perc-change-wrt-seassum-clim_native.csv?pr_july[(2025-01-01T12:00:00Z):1:(2090-01-01T12:00:00Z)][(-40.10297775):1:(-32.64199448)][(140.625):1:(150)]")
```

Percentage change evapotranspiration
```{r}
raw_evtr_jan_4.5_pc <- read.multi.line.header(file = "http://nrm-erddap.nci.org.au/erddap/griddap/wvap-morton_Amon_CSIRO-Mk3-6-0_rcp45_r1i1p1_perc-change-wrt-seassum-clim_native.csv?wvap_january[(2025-01-01T12:00:00Z):1:(2090-01-01T12:00:00Z)][(-40.10297775):1:(-32.64199448)][(140.625):1:(150)]")

raw_evtr_jan_8.5_pc <- read.multi.line.header(file = "http://nrm-erddap.nci.org.au/erddap/griddap/wvap-morton_Amon_CSIRO-Mk3-6-0_rcp85_r1i1p1_perc-change-wrt-seassum-clim_native.csv?wvap_january[(2025-01-01T12:00:00Z):1:(2090-01-01T12:00:00Z)][(-40.10297775):1:(-32.64199448)][(140.625):1:(150)]")

raw_evtr_jul_4.5_pc <- read.multi.line.header(file = "http://nrm-erddap.nci.org.au/erddap/griddap/wvap-morton_Amon_CSIRO-Mk3-6-0_rcp45_r1i1p1_perc-change-wrt-seassum-clim_native.csv?wvap_july[(2025-01-01T12:00:00Z):1:(2090-01-01T12:00:00Z)][(-40.10297775):1:(-32.64199448)][(140.625):1:(150)]")

raw_evtr_jul_8.5_pc <- read.multi.line.header(file = "http://nrm-erddap.nci.org.au/erddap/griddap/wvap-morton_Amon_CSIRO-Mk3-6-0_rcp85_r1i1p1_perc-change-wrt-seassum-clim_native.csv?wvap_july[(2025-01-01T12:00:00Z):1:(2090-01-01T12:00:00Z)][(-40.10297775):1:(-32.64199448)][(140.625):1:(150)]")
```

Convert data frames to rasters
```{r}
r_tmax_jan_4.5_ac <- rascc(raw_tmax_jan_4.5_ac, new.proj.layer = proj_mask)
r_tmax_jan_8.5_ac <- rascc(raw_tmax_jan_8.5_ac, new.proj.layer = proj_mask)
r_tmin_jul_4.5_ac <- rascc(raw_tmin_jul_4.5_ac, new.proj.layer = proj_mask)
r_tmin_jul_8.5_ac <- rascc(raw_tmin_jul_8.5_ac, new.proj.layer = proj_mask)

r_rain_jan_4.5_pc <- rascc(raw_rain_jan_4.5_pc, new.proj.layer = proj_mask)
r_rain_jan_8.5_pc <- rascc(raw_rain_jan_8.5_pc, new.proj.layer = proj_mask)
r_rain_jul_4.5_pc <- rascc(raw_rain_jul_4.5_pc, new.proj.layer = proj_mask)
r_rain_jul_8.5_pc <- rascc(raw_rain_jul_8.5_pc, new.proj.layer = proj_mask)

r_evtr_jan_4.5_pc <- rascc(raw_evtr_jan_4.5_pc, new.proj.layer = proj_mask)
r_evtr_jan_8.5_pc <- rascc(raw_evtr_jan_8.5_pc, new.proj.layer = proj_mask)
r_evtr_jul_4.5_pc <- rascc(raw_evtr_jul_4.5_pc, new.proj.layer = proj_mask)
r_evtr_jul_8.5_pc <- rascc(raw_evtr_jul_8.5_pc, new.proj.layer = proj_mask)
```



```{r}
plot(r_tmax_jan_4.5_ac[[1]])
```

```{r}
n_tmax_jan_4.5 <- as.numeric(sub("-.*", "", unique(raw_tmax_jan_4.5_ac$time)))
n_tmax_jan_8.5 <- as.numeric(sub("-.*", "", unique(raw_tmax_jan_8.5_ac$time)))
n_tmin_jul_4.5 <- as.numeric(sub("-.*", "", unique(raw_tmin_jul_4.5_ac$time)))
n_tmin_jul_8.5 <- as.numeric(sub("-.*", "", unique(raw_tmin_jul_8.5_ac$time)))

n_rain_jan_4.5 <- as.numeric(sub("-.*", "", unique(raw_rain_jan_4.5_pc$time)))
n_rain_jan_8.5 <- as.numeric(sub("-.*", "", unique(raw_rain_jan_4.5_pc$time)))
n_rain_jul_4.5 <- as.numeric(sub("-.*", "", unique(raw_rain_jul_4.5_pc$time)))
n_rain_jul_8.5 <- as.numeric(sub("-.*", "", unique(raw_rain_jul_4.5_pc$time)))

n_evtr_jan_4.5 <- as.numeric(sub("-.*", "", unique(raw_evtr_jan_4.5_pc$time)))
n_evtr_jan_8.5 <- as.numeric(sub("-.*", "", unique(raw_evtr_jan_4.5_pc$time)))
n_evtr_jul_4.5 <- as.numeric(sub("-.*", "", unique(raw_evtr_jul_4.5_pc$time)))
n_evtr_jul_8.5 <- as.numeric(sub("-.*", "", unique(raw_evtr_jul_4.5_pc$time)))
```


```{r}

```

