---
title: Illustrative Results of STEPS Population Viability Analysis for Leadbeater's
  Possum and Greater Glider
author: "GE Ryan - University of Melbourne"
output:
  pdf_document:
    fig_height: 6
    fig_width: 7
    fig_caption: true
    toc: yes
    toc_depth: 3
    includes:  
      in_header: header.tex
  word_document:
    toc: yes
    toc_depth: '3'
---

# Introduction


```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r}
source("R/spartan/spartan_settings.R")
```


```{r packages, results = 'hide', warning = FALSE, include = FALSE}
library(magrittr)
library(dplyr)
library(tibble)
library(sf)
library(lwgeom)
library(rgdal)
library(readr)
library(readxl)
library(ggplot2)
library(lubridate)
library(foreach)
library(doMC)
library(future)
library(future.apply)
library(tidyr)
library(gbm)
library(dismo)
library(steps)
library(raster)
library(rasterVis)
library(rlang)
library(viridis)
library(purrr)
library(rerddap)
library(knitr)
```

```{r load everything}
load(file = "output/RData/00_controls.RData")
load(file = "output/RData/01_landscape_variables.RData")
load(file = "output/RData/02_species_occurrences.RData")
load(file = "output/RData/03_LANDIS_variables.RData")
load(file = "output/RData/04_disturbance_variables.RData")
load(file = "output/RData/04.2_temporally_agg_dist_vars.RData")
load(file = "output/RData/05_geophys_vars.RData")
load(file = "output/RData/06_climate_variables.RData")
#load(file = "output/RData/07_combined_variables.RData")
load(file = "output/RData/09_fit_distribution_models.RData")
load(file = "output/RData/10_predict_SDMs_agg.RData")
load(file = "output/RData/11_pva.RData")
load(file = "output/RData/13.1a_mpc_all.RData")
```


```{r source all functions}
source(file = "R/functions/source.functions.R")
source.functions("R/functions")
```




```{r}
pa_data
```


```{r}
disturbance_variables
```

```{r}
disturbance_variables$landis_vars[[1]][[1]] %>% names
```

```{r}
disturbance_variables$dist_vars[[1]][[1]] %>% names
```


```{r}
temporally_agg_dist_vars
```

```{r}
temporally_agg_dist_vars$fire_ag[[1]]
```


```{r}
geo_vars
```


```{r}
clim_vars
```

```{r}
clim_vars$climate_projections[[1]][[1]]
```


```{r}
#var_set
```

```{r}
sdm_results
```

```{r}
sdm_results$brt.fit[[1]]
```


```{r}
pva_results_ch
```

Transition matrix
```{r}
pva_results_ch$tm[[1]]
```

```{r}

```


```{r}
#mpc_results_all_ch
```

here -old               scn_id
"BAU"                 = TH19_rcp45_PB_01
No harvest after 30 y = TH30_rcp45_PB_01
No harvest            = TH00_rcp45_PB_01


# LANDIS results

## Maximum age
Maximum age in years of any tree in 1 ha cell - direct output from LANDIS.

Large image is 2019, multi-plots are 10 year time-slices.

### Business as usual


OLD CODE
```{r max_age 1_01 bau, fig.cap = "Maximum age, business as usual scenario, 2019"}
max_age_1_01 <- lxtract(
  x = vgg1_1_01[c(1,11,21,31,41,51)],
  y = "max_age",
  layernames = sprintf("max_age_20%s9", 1:6)
)

lp(max_age_1_01, mm = 1)
```

NEW CODE
```{r}
max_age_1_01 <- lxtract(
  x = disturbance_variables$landis_vars[[1]][c(1,11,21,31,41,51)],
  y = "max_age",
  layernames = sprintf("max_age_20%s9", 1:6)
)

lp(max_age_1_01, mm = 1)
```



```{r, fig.cap = "Maximum age, business as usual scenario, 2069"}
lp(max_age_1_01, mm = 6)
```

```{r, fig.cap = "Maximum age, business as usual scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(max_age_1_01)
```


### No harvest after 30 years
```{r max_age 8_01 h30}
max_age_8_01 <- lxtract(
  x = vgg1_8_01[c(1,11,21,31,41,51)],
  y = "max_age",
  layernames = sprintf("max_age_20%s9", 1:6)
)
```

```{r fig.cap = "Maximum age, no harvest after 30 years scenario, 2019"}
lp(max_age_8_01, mm = 1)
```

```{r, fig.cap = "Maximum age, no harvest after 30 years scenario, 2069"}
lp(max_age_8_01, mm = 6)
```

```{r, fig.cap = "Maximum age, no harvest after 30 years scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(max_age_8_01)
```


### No harvest
```{r max_age 4_01 nth}
max_age_4_01 <- lxtract(
  x = vgg1_4_01[c(1,11,21,31,41,51)],
  y = "max_age",
  layernames = sprintf("max_age_20%s9", 1:6)
)
```

```{r, fig.cap = "Maximum age, no harvest scenario, 2019"}
lp(max_age_4_01, mm = 1)
```

```{r, fig.cap = "Maximum age, no harvest scenario, 2069"}
lp(max_age_4_01, mm = 6)
```

```{r, fig.cap = "Maximum age, no harvest scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(max_age_4_01)
```

## Old growth eucalypt biomass
Average biomass of old-growth eucalypt forest - trees >150 years of age - in 1km radius.

Single plot is 2019, multi-plots are 10 year time-slices.

### Business as usual
```{r biom_oge_1k 1_01 bau}
biom_oge_1k_1_01 <- lxtract(
  x = vgg1_1_01[c(1,11,21,31,41,51)],
  y = "biom_oge_1k",
  layernames = sprintf("OGbiom_20%s9", 1:6)
)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, business as usual scenario, 2019"}
lp(biom_oge_1k_1_01, mm = 1)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, business as usual scenario, 2069"}
lp(biom_oge_1k_1_01, mm = 6)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, business as usual scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(biom_oge_1k_1_01)
```

### No harvest after 30 years
```{r biom_oge_1k 8_01 h30}
biom_oge_1k_8_01 <- lxtract(
  x = vgg1_8_01[c(1,11,21,31,41,51)],
  y = "biom_oge_1k",
  layernames = sprintf("OGbiom_20%s9", 1:6)
)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, no harvest after 30 years scenario, 2019"}
lp(biom_oge_1k_8_01, mm = 1)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, no harvest after 30 years scenario, 2069"}
lp(biom_oge_1k_8_01, mm = 6)
```


```{r fig.cap = "Average biomass of old growth eucalypts in 1 km radius, no harvest after 30 years scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(biom_oge_1k_8_01)
```

### No harvest
```{r biom_oge_1k 4_01 nth}
biom_oge_1k_4_01 <- lxtract(
  x = vgg1_4_01[c(1,11,21,31,41,51)],
  y = "biom_oge_1k",
  layernames = sprintf("OGbiom_20%s9", 1:6)
)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, no harvest scenario, 2019"}
lp(biom_oge_1k_4_01, mm = 1)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, no harvest scenario, 2069"}
lp(biom_oge_1k_4_01, mm = 6)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, no harvest scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(biom_oge_1k_4_01)
```

## Acacia and midstorey biomass
Biomass of midstorey species and acacias important for Leadbeater's Possum.

### Business as usual
```{r lbm_biom 1_01 bau}
lbm_biom_1_01 <- lxtract(
  x = vlb1_1_01[c(1,11,21,31,41,51)],
  y = "lbm_biom",
  layernames = sprintf("lbm_biom_20%s9", 1:6)
)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, business as usual scenario, 2019"}
lp(lbm_biom_1_01, mm = 1)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, business as usual scenario, 2069"}
lp(lbm_biom_1_01, mm = 6)
```

```{r,   fig.cap = "Biomass of acacias and midstorey species, business as usual scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(lbm_biom_1_01)
```

### No harvest after 30 years
```{r lbm_biom 8_01 h30}
lbm_biom_8_01 <- lxtract(
  x = vlb1_8_01[c(1,11,21,31,41,51)],
  y = "lbm_biom",
  layernames = sprintf("lbm_biom_20%s9", 1:6)
)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, no harvest after 30 years scenario, 2019"}
lp(lbm_biom_8_01, mm = 1)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, no harvest after 30 years scenario, 2069"}
lp(lbm_biom_8_01, mm = 6)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, no harvest after 30 years scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(lbm_biom_8_01)
```


### No harvest
```{r lbm_biom 4_01 nth}
lbm_biom_4_01 <- lxtract(
  x = vlb1_4_01[c(1,11,21,31,41,51)],
  y = "lbm_biom",
  layernames = sprintf("lbm_biom_20%s9", 1:6)
)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, no harvest scenario, 2019"}
lp(lbm_biom_4_01, mm = 1)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, no harvest scenario, 2069"}
lp(lbm_biom_4_01, mm = 6)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, no harvest scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(lbm_biom_4_01)
```


# Disturbances

## Fires
Cells where fires occured over 10 year period, with large map showing 2019-2028, and multi-plot showing all following periods of 10 years.

Fires are stochasticaly generated based on fire weather and fuel loads in the simulated landscape, and each simulation has unique fire outcomes.

### Business as usual
```{r fire_1_01 bau, fig.cap = "Fires over 10 year period business as usual scenario, 2019-2028"}
lp(adv_1_01$fire[[1]], twocol = TRUE)
```

```{r, fig.cap = "Fires over 10 year period business as usual scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(adv_1_01$fire, twocol = TRUE)
```

### No harvest after 30 years
```{r fire_8_01 h30, fig.cap = "Fires over 10 year period no harvest after 30 years scenario, 2019-2028"}
lp(adv_8_01$fire[[1]], twocol = TRUE)
```

```{r, fig.cap = "Fires over 10 year period no harvest after 30 years scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(adv_8_01$fire, twocol = TRUE)
```

### No harvest
```{r fire_4_01 nth, fig.cap = "Fires over 10 year period no harvest scenario, 2019-2028"}
lp(adv_4_01$fire[[1]], twocol = TRUE)
```

```{r, fig.cap = "Fires over 10 year period no harvest scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(adv_4_01$fire, twocol = TRUE)
```

### Fires in time 50 (2068) in each LANDIS run
Fires in year 50 of all 30 LANDIS simulations (10 runs of each of the three scenarios) - illustratiing variation in fire occurrence in a single simulated timestep among simulations.

```{r}
fire_example <- expand.grid(
  scenario = scn_list,
  rep = rep_list
) %>%
  as_tibble %>%
  mutate(
    scn_id = paste0(scenario, "_", rep),
    dvid = paste0("dv_", scn_id)
  ) %>%
  rowwise %>%
  mutate(
    dv = map(
      .x = dvid,
      .f = get
    )
  ) %>%
  ungroup %>%
  mutate(
    fi = map(
      .x = dv,
      .f = function(x){
        y <- lapply(X = x, function(z){z[["fi"]]})
        
        y <- stack(y)
        
        return(y)
      }
    )
  ) %>%
  mutate(
    fi.50 = map(
      .x = fi,
      .f = ~.x[[50]]
    )
  ) %>%
  arrange(scenario)

firestack <- stack(fire_example$fi.50)
```

#### Business as usual
```{r, fig.cap = "Fires in 2068, business as usual scenario, simulations 1-6"}
lp(firestack[[1:6]], twocol = TRUE)
```

```{r, fig.cap = "Fires in 2068, business as usual scenario, simulations 7-10"}
lp(firestack[[7:10]], twocol = TRUE)
```

#### No harvest after 30 years
```{r, fig.cap = "Fires in 2068, no harvest after 30 years scenario , simulations 1-6"}
lp(firestack[[21:26]], twocol = TRUE)
```

```{r, fig.cap = "Fires in 2068, no harvest after 30 years scenario, simulations 7-10"}
lp(firestack[[27:30]], twocol = TRUE)
```

#### No harvest
```{r , fig.cap = "Fires in 2068, no harvest scenario, simulations 1-6"}
lp(firestack[[11:16]], twocol = TRUE)
```

```{r, fig.cap = "Fires in 2068, no harvest scenario, simulations 7-10"}
lp(firestack[[17:20]], twocol = TRUE)
```


## Timber harvest
Areas harvested in a 10 year period. Large image is 2019-2028, multi-plot is over all 10 year periods.

### Business as usual
```{r harvest_1_01 bau, fig.cap = "Timber harvest over 10 year period business as usual scenario, 2019-2028"}
lp(adv_1_01$harvest[[1]], twocol = TRUE)
```

```{r, fig.cap = "Timber harvest over 10 year period business as usual scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(adv_1_01$harvest, twocol = TRUE)
```

### No harvest after 30 years
```{r harvest_8_01 h30, fig.cap = "Timber harvest over 10 year period no harvest after 30 years scenario, 2019-2028"}
lp(adv_8_01$harvest[[1]], twocol = TRUE)
```

```{r, fig.cap = "Timber harvest over 10 year period no harvest after 30 years scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(adv_8_01$harvest, twocol = TRUE)
```

### No harvest
```{r harvest_4_01 nth, fig.cap = "Timber harvest over 10 year period no harvest scenario, 2019-2028"}
lp(adv_4_01$harvest[[1]], twocol = TRUE)
```

```{r, fig.cap = "Timber harvest over 10 year period no harvest scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(adv_4_01$harvest, twocol = TRUE)
```


## Planned burning
Areas burnt through planned burning in a 10 year period. Large image is 2019-2028, multi-plot is over all 10 year periods.

### Business as usual
```{r pb_1_01 bau, fig.cap = "Planned burning over 10 year period business as usual scenario, 2019-2028"}
lp(adv_1_01$PB[[1]], twocol = TRUE)
```

```{r, fig.cap = "Planned burning over 10 year period business as usual scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(adv_1_01$PB, twocol = TRUE)
```

### No harvest after 30 years
```{r pb_8_01 h30, fig.cap = "Planned burning over 10 year period no harvest after 30 years scenario, 2019-2028"}
lp(adv_8_01$PB[[1]], twocol = TRUE)
```

```{r, fig.cap = "Planned burning over 10 year period no harvest after 30 years scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(adv_8_01$PB, twocol = TRUE)
```

### No harvest
```{r pb_4_01 nth, fig.cap = "Planned burning over 10 year period no harvest scenario, 2019-2028"}
lp(adv_4_01$PB[[1]], twocol = TRUE)
```

```{r, fig.cap = "Planned burning over 10 year period no harvest scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(adv_4_01$PB, twocol = TRUE)
```

## Total burnt and harvested
```{r, cache = TRUE}
sims_table <- expand.grid(
  scenario = scn_list,
  rep = rep_list
) %>%
  as_tibble %>%
  rowwise %>%
  mutate(
    dv = map(
      .f = get,
      .x = sprintf(
        "dv_%s_%s",
        scenario,
        rep
      )
    )
  )%>%
  ungroup %>%
  mutate(
    fi = map(
      .f = lapply,
      .x = dv,
      FUN = function(x){x[["fi"]]}
    ),
    fi  = map(
      
      .f = stack,
      .x = fi
     )
  )


sims_table <- sims_table %>%
  mutate(
    fi.sum = map(
      .f = function(x){
        sum(getValues(x), na.rm = TRUE)
      },
      .x = fi
    )
  )


sims_table <- unnest(sims_table, cols = fi.sum) %>%
  mutate(
    scenario = case_when(scenario == 1 ~ "BAU",
                         scenario == 4 ~ "No harvest",
                         scenario == 8 ~ "Cease harvest Y30")
  )


sims_table <- sims_table %>%
  mutate(
    lo = map(
      .f = lapply,
      .x = dv,
      FUN = function(x){x[["lo"]]}
    ),
    lo  = map(
      
      .f = stack,
      .x = lo
     )
  )


sims_table <- sims_table %>%
  mutate(
    lo.sum = map(
      .f = function(x){
        sum(getValues(x), na.rm = TRUE)
      },
      .x = lo
    )
  )

sims_table <- unnest(sims_table, cols = lo.sum)
```

```{r, fig.cap="Total area burnt in each LANDIS simulation, by scenario type."}
ggplot(sims_table, aes(x = scenario, y = fi.sum)) +
  geom_boxplot() +
  geom_point(aes(colour = rep), position = position_jitter(width = 0.1, height = 0)) 
```

```{r, fig.cap = "Total area harvested in each LANDIS simulation, by scenario type."}
ggplot(sims_table, aes(x = scenario, y = lo.sum)) +
  geom_boxplot() +
  geom_point(aes(colour = rep), position = position_jitter(width = 0.1, height = 0)) 
```

# Climate

## Precipitation

### January, RCP 4.5
Rainfall in January, large image is 2019, multi-plot shows 10 year time-slices.

```{r precipJan4.5}
precipJan4.5 <- lxtract(
  x = vgg1_4_01[c(1,11,21,31,41,51)],
  y = "prec01",
  layernames = sprintf("PrJan_20%s9", 1:6)
)
```

```{r, fig.cap= "Rainfall, January, 2019"}
lp(precipJan4.5,
   mm = 1)
```

```{r, fig.cap = "Rainfall, January, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(precipJan4.5)
```

### July, RCP 4.5
Rainfall in July, large image is 2019, multi-plot shows 10 year time-slices.

```{r precipJul4.5}
precipJul4.5 <- lxtract(
  x = vgg1_4_01[c(1,11,21,31,41,51)],
  y = "prec07",
  layernames = sprintf("PrJul_20%s9", 1:6)
)
```

```{r, fig.cap = "Rainfall, July, 2019"}
lp(precipJul4.5, mm = 6)
```

```{r, fig.cap= "Rainfall, July, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(precipJul4.5)
```


## Temperature

### January, maximum temperature, RCP 4.5
Large image is 2019, multi-plot shows 10 year time-slices.

```{r tmaxJan4.5}
tmaxJan4.5 <- lxtract(
  x = vgg1_4_01[c(1,11,21,31,41,51)],
  y = "tmax01",
  layernames = sprintf("tmaxJan_20%s9", 1:6)
)
```

```{r, fig.cap = "Maximum temperature, January, 2019"}
lp(tmaxJan4.5, mm = 1)
```

```{r, fig.cap = "Maximum temperature, January, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(tmaxJan4.5)
```

### July, minumum temperature, RCP 4.5
Large image is 2019, multi-plot shows 10 year time-slices.

```{r tminJul4.5}
tminJul4.5 <- lxtract(
  x = vgg1_4_01[c(1,11,21,31,41,51)],
  y = "tmin07",
  layernames = sprintf("tminJul_20%s9", 1:6)
)
```

```{r, fig.cap="Minimum temerature, July, 2019"}
lp(tminJul4.5, mm = 1)
```


```{r fig.cap="Minimum temperature, July, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(tminJul4.5)
```



# Leadbeater's Possum results

## Species distribution model

Summary information for Leadbeater's possum species distribution model.

Variables are, in order:

- maximum January temperature,
- January rainfall,
- maximum age of trees,
- log vertical distance from major waterways,
- July minimum temperature,
- proportion of midstorey biomass,
- total midstorey biomass,
- July rainfall,
- log vertical distance from minor waterways,
- proportion of biomass >150 years old,
- log vertical distance from salt waterway,
- anisotronic heating x ruggedness, thorium,
- log vertical distance from any waterway,
- proportion of old growth biomass in surrounding 3 ha x 3ha area,
- total biomass of old growth forest in surrounding 3 ha x 3 ha area 

```{r, fig.cap="Percentage contribution of Leadbeater's possum distribution model"}
summary(brt_lb$brt.fit[[11]])
```

```{r, fig.cap="Partial dependence plot for Leadbeater's possum species distribution model"}
gbm.plot(brt_lb$brt.fit[[11]])
```


```{r sdm 1_01 bau lb, fig.cap="Baseline species distribution model for Leadbeater's possum"}
plb_1_01 <- preds_lb_agg$predmaps[[1]][[c(1,11,21,31,41,51)]]

names(plb_1_01) <- sprintf("sdm_20%s9", 1:6)

lp(plb_1_01[[1]])
```

```{r, fig.cap="Baseline species distribution model for Leadbeater's possum, with presence (yellow) and absence (blue) records overlaid"}
plot(plb_1_01[[1]], col = magma(16))
plot(pa_lb_09b %>% dplyr::select(-date), pch = 20, cex = 0.3,  add = TRUE)
```

### SDM spatial predictions

### Business as usual
```{r, fig.cap = "Species distribution model for Leadbeater's possum, business as usual scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(plb_1_01)
```

### No harvest after 30 years
```{r sdm 8_01 h30 lb, fig.cap = "Species distribution model for Leadbeater's possum, no harvest after 30 years scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
plb_8_01 <- preds_lb_agg$predmaps[[3]][[c(1,11,21,31,41,51)]]

names(plb_8_01) <- sprintf("sdm_20%s9", 1:6)

lp(plb_8_01)
```

### No harvest
```{r sdm 4_01 nth lb, fig.cap = "Species distribution model for Leadbeater's possum, no harvest scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
plb_4_01 <- preds_lb_agg$predmaps[[2]][[c(1,11,21,31,41,51)]]

names(plb_4_01) <- sprintf("sdm_20%s9", 1:6)

lp(plb_4_01)
```


## Populaition viability analysis

## All life stages
Population for each life history stage over 100 simulations for a single LANDIS simulation of each management scenario.

Coloured lines are mean, grey lines are population over a single simulation. Panels are newborn (left), juvenile (middle), and adult (right) populations.

### Business as usual
```{r pop all stages 1_01 bau lb, fig.cap = "Newborn, juvenile, and adult populations of Leadbeater's possum, business as usual scenario"}
psr(simset_lb$pva_pops[[1]])
```

```{r}
psr(pva_results_ch$pva[[1]])
```



### No harvest after 30 years
```{r pop all stages 8_01 h30 lb, fig.cap = "Newborn, juvenile, and adult populations of Leadbeater's possum, no harvest after 30 years scenario"}
psr(simset_lb$pva_pops[[3]])
```

### No harvest
```{r pop all stages 4_01 nth lb, fig.cap = "Newborn, juvenile, and adult populations of Leadbeater's possum, no harvest scenario"}
psr(simset_lb$pva_pops[[2]])
```

## Total population

Total population for each of 100 PVA simulations for a single LANDIS simulation of each management scenario.

Dark grey line is mean, grey ribbon is 95% bound of simulated population size, and light grey lines are population over a single PVA simulation. Dotted line below is the expected minimum population size, which is red when it equals zero.

### Business as usual
```{r pop total 1_01 bau lb, fig.cap = "Total populationof Leadbeater's possum, business as usual scenario"}
psr(simset_lb$pva_pops[[1]], stages = 0, ylim = c(0, 5000))
```

### No harvest after 30 years
```{r pop total 8_01 h30 lb, fig.cap = "Total populationof Leadbeater's possum, no harvest after 30 years scenario"}
psr(simset_lb$pva_pops[[3]], stages = 0, ylim = c(0, 5000))
```

### No harvest
```{r pop total 4_01 nth lb, fig.cap = "Total populationof Leadbeater's possum, no harvest scenario"}
psr(simset_lb$pva_pops[[2]], stages = 0, ylim = c(0, 5000))
```

## Spatial population
Population as distributed in space. First multi-plot is the initial population in each life-history stage, and second multi-plot is the simulated total population at 10-year time-slices.

### Business as usual
```{r, fig.cap = "Initial population of Leadbeater's possum, Business as usual scenario"}
lp(simset_lb$init_pop[[1]])
```

```{r spat pop adult 1_01 bau lb, fig.cap = "Total population of Leadbeater's possum, business as usual scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
psr_raster(simset_lb$pva_sims[[1]], timesteps = c(1,10,20,30,40,50))
```

### No harvest after 30 years
```{r, fig.cap = "Initial population of Leadbeater's possum, no harvest after 30 years scenario"}
lp(simset_lb$init_pop[[2]])
```


```{r spat pop 8_01 h30 lb, fig.cap = "Total population of Leadbeater's possum, no harvest after 30 years scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
psr_raster(simset_lb$pva_sims[[2]], timesteps = c(1,10,20,30,40,50))
```

### No harvest
```{r, fig.cap = "Initial population of Leadbeater's possum, no harvest scenario"}
lp(simset_lb$init_pop[[3]])
```

```{r spat pop 4_01 nth lb, fig.cap = "Total population of Leadbeater's possum, no harvest scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
psr_raster(simset_lb$pva_sims[[3]], timesteps = c(1,10,20,30,40,50))
```

# Greater Glider



## Species distribution model

Summary information for greater glider species distribution model.

Variables are, in order:

- maximum age of trees,
- January rainfall,
- July minimum temperature,
- July rainfall,
- thorium,
- log vertical distance from major waterways,
- anisotronic heating x ruggedness, thorium,
- biomass of greater glider food tree species,
- log vertical distance from minor waterways,
- log vertical distance from any waterway,
- proportion of biomass of greater glider food tree species,
- proportion of biomass >150 years old,
- proportion of old growth biomass in surrounding 1 km radius,
- biomass of old growth known greater glider den tree species,
- maximum January temperature,
- total old growth biomass in surrounding 1 km radius,
- log vertical distance from salt waterway,
- proportion biomass of old growth known greater glider den tree species.

```{r, fig.cap="Percentage contribution of greater glider distribution model"}
summary(brt_gg$brt.fit[[11]])
```

```{r, fig.cap="Partial dependence plot for greater glider species distribution model"}
gbm.plot(brt_gg$brt.fit[[11]])
```


```{r sdm 1_01 bau gg, fig.cap="Baseline species distribution model for greater glider"}
pgg_1_01 <- preds_gg_agg$predmaps[[1]][[c(1,11,21,31,41,51)]]

names(pgg_1_01) <- sprintf("sdm_20%s9", 1:6)

lp(pgg_1_01[[1]])
```

```{r, fig.cap="Baseline species distribution model for greater glider, with presence (yellow) and absence (blue) records overlaid"}
plot(pgg_1_01[[1]], col = magma(16))
plot(pa_gg_09b %>% dplyr::select(-date), pch = 20, cex = 0.3,  add = TRUE)
```

### SDM spatial predictions

### Business as usual
```{r, fig.cap = "Species distribution model for greater glider, business as usual scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(pgg_1_01)
```

### No harvest after 30 years
```{r sdm 8_01 h30 gg, fig.cap = "Species distribution model for greater glider, no harvest after 30 years scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
pgg_8_01 <- preds_gg_agg$predmaps[[3]][[c(1,11,21,31,41,51)]]

names(pgg_8_01) <- sprintf("sdm_20%s9", 1:6)

lp(pgg_8_01)
```

### No harvest
```{r sdm 4_01 nth gg, fig.cap = "Species distribution model for greater glider, no harvest scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
pgg_4_01 <- preds_gg_agg$predmaps[[2]][[c(1,11,21,31,41,51)]]

names(pgg_4_01) <- sprintf("sdm_20%s9", 1:6)

lp(pgg_4_01)
```


## Populaition viability analysis

## All life stages
Population for each life history stage over 100 simulations for a single LANDIS simulation of each management scenario.

Coloured lines are mean, grey lines are population over a single simulation. Panels are newborn (left), juvenile (middle), and adult (right) populations.

### Business as usual
```{r pop all stages 1_01 bau gg, fig.cap = "Newborn, juvenile, and adult populations of greater glider, business as usual scenario"}
psr(simset_gg$pva_pops[[1]])
```

### No harvest after 30 years
```{r pop all stages 8_01 h30 gg, fig.cap = "Newborn, juvenile, and adult populations of greater glider, no harvest after 30 years scenario"}
psr(simset_gg$pva_pops[[3]])
```

### No harvest
```{r pop all stages 4_01 nth gg, fig.cap = "Newborn, juvenile, and adult populations of greater glider, no harvest scenario"}
psr(simset_gg$pva_pops[[2]])
```

## Total population

Total population for each of 100 PVA simulations for a single LANDIS simulation of each management scenario.

Dark grey line is mean, grey ribbon is 95% bound of simulated population size, and light grey lines are population over a single PVA simulation. Dotted line below is the expected minimum population size, which is red when it equals zero.

### Business as usual
```{r pop total 1_01 bau gg, fig.cap = "Total populationof greater glider, business as usual scenario"}
psr(simset_gg$pva_pops[[1]], stages = 0, ylim = c(0, 10000))
```

### No harvest after 30 years
```{r pop total 8_01 h30 gg, fig.cap = "Total populationof greater glider, no harvest after 30 years scenario"}
psr(simset_gg$pva_pops[[3]], stages = 0, ylim = c(0, 10000))
```

### No harvest
```{r pop total 4_01 nth gg, fig.cap = "Total populationof greater glider, no harvest scenario"}
psr(simset_gg$pva_pops[[2]], stages = 0, ylim = c(0, 10000))
```

## Spatial population
Population as distributed in space. First multi-plot is the initial population in each life-history stage, and second multi-plot is the simulated total population at 10-year time-slices.

### Business as usual
```{r, fig.cap = "Initial population of greater glider, Business as usual scenario"}
lp(simset_gg$init_pop[[1]])
```

```{r spat pop adult 1_01 bau gg, fig.cap = "Total population of greater glider, business as usual scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
psr_raster(simset_gg$pva_sims[[1]], timesteps = c(1,10,20,30,40,50))
```

### No harvest after 30 years
```{r, fig.cap = "Initial population of greater glider, no harvest after 30 years scenario"}
lp(simset_gg$init_pop[[2]])
```


```{r spat pop 8_01 h30 gg, fig.cap = "Total population of greater glider, no harvest after 30 years scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
psr_raster(simset_gg$pva_sims[[2]], timesteps = c(1,10,20,30,40,50))
```

### No harvest
```{r, fig.cap = "Initial population of greater glider, no harvest scenario"}
lp(simset_gg$init_pop[[3]])
```

```{r spat pop 4_01 nth gg, fig.cap = "Total population of greater glider, no harvest scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
psr_raster(simset_gg$pva_sims[[3]], timesteps = c(1,10,20,30,40,50))
```
