---
title: "fire_sum"
output: html_document
---

```{r}
library(dplyr)
library(ggplot2)
#library(lme4)
```


```{r}
load(file = "output/RData/fire_sum_ch.RData")
load(file = "output/RData/pva_summary_ch.RData")
load(file = "output/RData/19_mpc_results_summary.RData")
```

## Fire data
Fire sum is sum fire over all years in each LANDIS run
```{r}
fire_sum
```

Per year
```{r}
fire_sum_year
```

Weighted by year
```{r}
fire_sum_weighted <- fire_sum_weighted %>%
  group_by(scn_id) %>%
  summarise(fire_weighted_sum = sum(fire_weighted))

fire_sum_weighted
```
## Metapopulation capacity data
Metapopulation capacity data

Each mpc measure by year
- mpc is the best response here - using maxumum sum sensitiy and specificity
- mpc_05 and mpc_07 correspond to alternate measures of metapopulation capacity

This data set has 4 climate models for PVA species, but only 1 for metapopulation capacity only species 

```{r}
mpc_r_ch
```
2 useable subsets:

pva only spp with 4 climate models
```{r}
mpc_r_ch %>%
  filter(sp_group == "PVA")
```

of all species and only ACCESS1-0 climate model
```{r}
mpc_r_ch %>%
  filter(climate_model == "ACCESS1-0")
```


Summary of metapopulation capacity
r_ values ar references corresponding to TH19_rcp45_PB scenario (median).
delta is value - ref

dp (delta proportion) = (value-ref)/ref

dp is probably the measure to use

dp_median
 or dp_min probably?


```{r}
mpc_rs
```

## PVA data
emp is minimum population of the 100 sims

emp_95 is 5th%ile value population of 100 sims
```{r}
pva_r_ch
```


LANDIS runs = metapopulation capacity (only) speices
- 6 management scenarios
  - 10 replicate runs of each
  
Management scenarios vary
  - harvesting - ongoing (1), stop in 2030 (2), none (3)
  - carbon pathway / climate change (4 rcp 4.5, 2 rcp 8.5)
  - planned burning (5 yes, 1 no)

```{r}
unique(pva_r_ch$scn)
```

PVA species
- 4 climate models
- 100 sims in each pva



```{r}
fire_pva <- full_join(
  x = pva_r_ch,
  y = fire_sum,
  by = "scn_id"
)
fire_pva
```

```{r}
ggplot(data = fire_pva) +
  geom_point(
    aes(
      x = fire,
    y = prop_extant,
    shape = scenario
    )
  ) +
  facet_wrap(~sp, scales = "free_y")
```


```{r}
glm_emp <- glm(
  emp ~ fire + sp + rcp + harvest_scenario + climate_model + fire*sp + rcp*sp +climate_model*sp + harvest_scenario*sp, data = fire_pva,
  family = gaussian
)
```


```{r}
summary(glm_emp)
```

```{r}
glm_prop_extant <- glm(
  prop_extant ~ fire + sp + rcp + harvest_scenario + climate_model + fire*sp + rcp*sp +climate_model*sp + harvest_scenario*sp, data = fire_pva,
  family = gaussian
)
```


```{r}
summary(glm_prop_extant)
```