---
title: "Forest Futures Analysis"
output: html_notebook:
  toc: true
  toc_depth: 3
author: GE Ryan
date: 20190827
---

# Setup and data preparation

## Controls and software

### Packages
```{r packages}
library(magrittr)
library(dplyr)
library(tibble)
library(sf)
library(lwgeom)
library(rgdal)
library(readr)
library(readxl)
library(ggplot2)
library(lubridate)
library(foreach)
library(doMC)
library(future)
library(future.apply)
library(tidyr)
library(dismo)
library(gbm)
library(steps)
library(raster)
library(rasterVis)
library(rlang)
library(viridis)
```

```{r load everything}
load(file = "output/RData/00_comp_controls.RData")
load(file = "output/RData/01_landscape_variables.RData")
load(file = "output/RData/02_species_occurrences.RData")
load(file = "output/RData/03_LANDIS_variables.RData")
load(file = "output/RData/04_disturbance_variables.RData")
load(file = "output/RData/05_geophys_vars.RData")
load(file = "output/RData/06_climate_variables.RData")
load(file = "output/RData/07_combined_variables.RData")
load(file = "output/RData/08_distribution_model_data.RData")
#load(file = "output/RData/")
```


### Functions
```{r source all functions}
source(file = "R/functions/source.functions.R")
source.functions("R/functions")
```


### Paths
```{r proj_paths}
proj_path <- "/home/unimelb.edu.au/ryange/rfst"
# proj_path <- "D:/Users/ryan/Dropbox/Work/RFA_STEPS/rfst/"
```

### Start year
```{r year0}
year0 <- 2019
```

### Timesteps
```{r ntimesteps}
ntimesteps <- 50
```

### Cores to use
```{r ncores}
ncores <- 20
```

### LANDIS scenarios
```{r LANDIS scenarios}
scn_list <- c("1", "4", "8")
rep_list <- sprintf("%02d", 1:10)
```


### Save computing controls
```{r save computing controls}
save(proj_path,
     year0,
     ntimesteps,
     ncores,
     scn_list,
     rep_list,
     source.functions,
     file = "output/RData/00_comp_controls.RData")
```


### Image controls

#### Png controls
```{r png controls}
res <- 600
width.png <- 3200
height.png <- 2000
```


## Landscape
```{r source landscape}
#source(file = "R/01_landscape_variables.R")
```

```{r load landscape vars}
load(file = "output/RData/01_landscape_variables.RData")
```

Mask of central highlands
```{r plot ch_mask}
lp(ch_mask)
```
LANDIS Ecoregions
```{r plot ch_eco}
lp(ch_eco)
```
Fire ecoregions
```{r plot ch_fire_eco}
lp(ch_fire_eco)
```
LANDIS initial conditions
```{r plot ch_ic}
lp(ch_ic)
```
Management zones
```{r plot ch_mgt}
lp(ch_mgt)
```
Aspect
```{r plot ch_aspect}
lp(ch_aspect)
```
Slope
```{r plot ch_slope}
lp(ch_slope)
```
Stand classifications
```{r plot ch_stands}
lp(ch_stands)
```
Fire history
```{r plot ch_fire_history}
lp(ch_fire_history)
```

Logging history
```{r plot logging history}
lp(ch_logging_history)
```


## Species occurrences

```{r source species occurrences}
#source(file = "R/02_species_occurrence.R")
```

```{r load species occurrences}
load(file = "output/RData/02_species_occurrences.RData")
```

```{r plot pa_lb_09}
ggplot() +
  geom_sf(data = ch_rfa) +
  geom_sf(data = pa_lb_09, aes(col = as.factor(PA), alpha = date))
```

```{r plot pa_lb_80}
ggplot() +
  geom_sf(data = ch_rfa) +
  geom_sf(data = pa_lb_80, aes(col = as.factor(PA), alpha = date))
```

```{r plot pa_gg_09}
ggplot() +
  geom_sf(data = ch_rfa) +
  geom_sf(data = pa_gg_09, aes(col = as.factor(PA), alpha = date))
```

```{r plot pa_gg_80}
ggplot() +
  geom_sf(data = ch_rfa) +
  geom_sf(data = pa_gg_80, aes(col = as.factor(PA), alpha = date))
```

## LANDIS outputs
```{r source LANDIS variables}
#source(file = "R/03_LANDIS_variables.R")
```

```{r load LANDIS variables}
load(file = "output/RData/03_LANDIS_variables.RData")
```

### Scenario 1: BAU: Timber harvesting, planned burning, climate change RCP 4.5
```{r}
lp(lv_1_01[[1]])
```
```{r}
levelplot(lv_1_01[[1]][[1]], margin = FALSE)
```

```{r}
levelplot(lv_1_01[[1]][[15]], margin = FALSE)
```

```{r}
levelplot(lv_1_01[[1]][[20]], margin = FALSE)
```
```{r}
levelplot(lv_1_01[[1]][[13]], margin = FALSE)
```

```{r}
levelplot(lv_1_01[[51]][[13]], margin = FALSE)
```

```{r}
levelplot(lv_4_01[[51]][[13]], margin = FALSE)
```

```{r}
levelplot(lv_8_01[[51]][[13]], margin = FALSE)
```

```{r}
levelplot(lv_4_01[[3]][[19]], margin = FALSE)
```
```{r}
levelplot(lv_4_01[[3]][[13]], margin = FALSE)
```

```{r}
levelplot(lv_4_01[[4]][[13]], margin = FALSE)
```




## Disturbance variables
```{r source landscape_variables}
#source(file = "R/04_disturbance_variables.R")
```


```{r load disturbance variables}
load(file = "output/RData/04_disturbance_variables.RData")
```

Logging history
```{r plot logging history s1}
lp(stack(dv_1_01[[1]][[6]], dv_1_01[[51]][[6]]))
```

```{r plot logging history s1}
lp(stack(dv_8_01[[1]][[4]], dv_8_01[[51]][[4]]))
```

```{r}
lp(stack(dv_8_01[[1]][[2]], dv_8_01[[51]][[2]]))
```
```{r}
lp(stack(dv_8_01[[1]][[3]], dv_8_01[[51]][[3]]))
```

```{r}
lp(stack(dv_8_01[[1]][[4]], dv_8_01[[51]][[4]]))
```



## Geoophysical variables
```{r source geophysical variables}
#source(file = "R/05_geophysical_variables.R")
```

```{r load geophysicial variables}
load(file = "output/RData/05_geophys_vars.RData")
```

## Climatic variables
```{r source climate variables}
source(file = "R/06_climate_variables.R")
```

```{r load climate variables}
load(file = "output/RData/06_climate_variables.RData")
```


## 07 Combined variables
```{r source combined variables}
#source(file = "R/07_combined_variables.R")
```


```{r load combined variables}
load(file = "output/RData/07_combined_variables.RData")
```
## 08 Distribution model data
```{r source distrinbution model data}
#source(file = "R/08_distribution_model_data.R")
```

```{r load distribution model data}
load(file = "output/RData/08_distribution_model_data.RData")
```



# Distribution modelling

## Leadbeater's Possum

### Table of models
```{r lbp dist table}
dt_lb <- tibble(year.from = c(80, 09),
                bg = c(TRUE, FALSE),
                varset = list(vn_lb_1, vn_lb_2)) %>%
  expand(year.from, bg, varset) %>%
  rowwise %>%
  mutate(pa.data = list(get(sprintf("pa_lb_%02d%s", year.from, ifelse(bg, "", "x"))))) %>%
  mutate(model.data = map(.x = get.model.data,
                          .f = pa.data))

dt_lb
```
```{r}
aa <- get.model.data(pa_lb_09, vars_1_01, na.omit = FALSE)

aa
```

```{r}
clean.model.data(aa, y = vn_lb_1)
```


```{r}
get.model.data(pa_lb_09, vars_1_01, na.omit = FALSE) %>%
  mutate(nd = as.numeric(ymd("2019-01-01") - date)/365,
         nd = ifelse(nd > 0, nd, 0)) %>%
  mutate(tsf = tsf - nd,
         tsl = tsl - nd,
         max_age = max_age - nd) %>%
  mutate(max_age = case_when(tsf < 0 ~ NA_real_,
                             tsl < 0 ~ NA_real_,
                             max_age < 0 ~ NA_real_,
                             TRUE ~ max_age)) %>%
  mutate(tsf = ifelse(tsf >= 0, tsf, NA),
         tsl = ifelse(tsl >= 0, tsl, NA))
```

```{r}
aa <- tibble(a = 1:10, b = 2:11, c = 5:14)

aa
```


```{r}
zz <- function(x, y){
  
  result <- x %>%
    dplyr::select(a, y)
  
  return(result)
}
```



```{r}
zz(aa, c("b"))
```

```{r}
zz(mtcars, c("cyl", "mpg"))
```



```{r}
colnames(md_lb_09)
```
```{r}
brt_lb09_n <- gbm.step(data = nd_lb_09,
                     gbm.x = c(3, 15, 17, 30:39),
                     gbm.y = 2,
                     family = "bernoulli",
                     tree.complexity = 5,
                    learning.rate = 0.1,
                    step.size = 1,
                    bag.fraction = 0.5,
                    prev.stratify = FALSE,
                    verbose = FALSE,
                    max.trees = 2000)
```

```{r}
brt_lb09_m <- gbm.step(data = md_lb_09,
                     gbm.x = c(3, 15, 17, 30:39),
                     gbm.y = 2,
                     family = "bernoulli",
                     tree.complexity = 5,
                    learning.rate = 0.01,
                    step.size = 1,
                    bag.fraction = 0.5,
                    prev.stratify = FALSE,
                    verbose = FALSE,
                    max.trees = 2000)
```


```{r}
ip_lb09_n <- brtpredict(variables = v_1_01,
                      model = brt_lb09_n,
                      scn_id = "ip",
                      varset = "test",
                      species = "lb")
```

```{r}
plot(ip_lb09_n)
```


```{r}
ip_lb09_m <- brtpredict(variables = v_1_01,
                      model = brt_lb09_m,
                      scn_id = "ip",
                      varset = "test",
                      species = "lb")
```

```{r}
plot(ip_lb09_m)
```


# Population viability analysis 

  

```{r}
lp(aa)
```


```{r}
plot(aa, col = viridis(100, option = "A"))
plot(pa_lb_09, add = TRUE)
```

