---
title: "Forest Futures Analysis"
output: html_notebook:
  toc: true
  toc_depth: 3
author: GE Ryan
date: 20190827
---

# Setup and data preparation

## Controls and software

### Packages
```{r packages}
library(magrittr)
library(dplyr)
# library(tibble)
library(sf)
library(lwgeom)
library(rgdal)
library(readr)
library(readxl)
library(ggplot2)
library(lubridate)
library(foreach)
library(doMC)
library(future)
library(future.apply)
library(tidyr)
library(dismo)
library(gbm)
library(steps)
library(raster)
library(rasterVis)
library(viridis)
```

### Functions
```{r functions}
source(file = "R/functions/bind.simulation.repetitions.R")
source(file = "R/functions/brtpredict.R")
source(file = "R/functions/gbmstep.R")
#source(file = "R/functions/get.disturbance.R")
source(file = "R/functions/get.dist.R")
source(file = "R/functions/get.landis.vars.R")
source(file = "R/functions/get.stable.states.R")
source(file = "R/functions/gpr.R")
source(file = "R/functions/gps.R")
source(file = "R/functions/initpop.R")
source(file = "R/functions/interpolate.climdat.R")
source(file = "R/functions/lp.R")
source(file = "R/functions/parsim.R")
source(file = "R/functions/pg.pa.R")
source(file = "R/functions/pg.sf.R")
source(file = "R/functions/proc.vba.R")
source(file = "R/functions/psr.R")
source(file = "R/functions/rascc.R")
source(file = "R/functions/read.multi.line.header.R")
source(file = "R/functions/read.vba.R")
source(file = "R/functions/rmax.R")
source(file = "R/functions/round.extent.R")
source(file = "R/functions/rst.op.R")
source(file = "R/functions/stackbrtpred.R")
```

```{r source all functions}
source(file = "R/functions/source.functions.R")
source.functions("R/functions")
```


### Paths
```{r proj_paths}
proj_path <- "/home/unimelb.edu.au/ryange/rfst"
# proj_path <- "D:/Users/ryan/Dropbox/Work/RFA_STEPS/rfst/"
```

### Start year
```{r year0}
year0 <- 2019
```

### Timesteps
```{r ntimesteps}
ntimesteps <- 50
```

### Cores to use
```{r ncores}
ncores <- 20
```

### LANDIS scenarios
```{r LANDIS scenarios}
scn_list <- c("1", "4", "8")
rep_list <- sprintf("%02d", 1:10)
```


### Save computing controls
```{r save computing controls}
save(proj_path,
     year0,
     ntimesteps,
     ncores,
     scn_list,
     rep_list,
     source.functions,
     file = "output/RData/00_comp_controls.RData")
```


### Image controls

#### Png controls
```{r png controls}
res <- 600
width.png <- 3200
height.png <- 2000
```


## Landscape
```{r source landscape}
#source(file = "R/01_landscape_variables.R")
```

```{r load landscape vars}
load(file = "output/RData/01_landscape_variables.RData")
```

Mask of central highlands
```{r plot ch_mask}
lp(ch_mask)
```
LANDIS Ecoregions
```{r plot ch_eco}
lp(ch_eco)
```
Fire ecoregions
```{r plot ch_fire_eco}
lp(ch_fire_eco)
```
LANDIS initial conditions
```{r plot ch_ic}
lp(ch_ic)
```
Management zones
```{r plot ch_mgt}
lp(ch_mgt)
```
Aspect
```{r plot ch_aspect}
lp(ch_aspect)
```
Slope
```{r plot ch_slope}
lp(ch_slope)
```
Stand classifications
```{r plot ch_stands}
lp(ch_stands)
```
Fire history
```{r plot ch_fire_history}
lp(ch_fire_history)
```

Logging history
```{r plot logging history}
lp(ch_logging_history)
```


## Species occurrences


## LANDIS outputs
```{r source LANDIS variables}
#source(file = "R/03_LANDIS_variables.R")
```

```{r load LANDIS variables}
load(file = "output/RData/03_LANDIS_variables.RData")
```

### Scenario 1: BAU: Timber harvesting, planned burning, climate change RCP 4.5
```{r}
lp(lv_1_01[[1]])
```
```{r}
levelplot(lv_1_01[[1]][[1]], margin = FALSE)
```

```{r}
levelplot(lv_1_01[[1]][[15]], margin = FALSE)
```

```{r}
levelplot(lv_1_01[[1]][[20]], margin = FALSE)
```
```{r}
levelplot(lv_1_01[[1]][[13]], margin = FALSE)
```

```{r}
levelplot(lv_1_01[[51]][[13]], margin = FALSE)
```

```{r}
levelplot(lv_4_01[[51]][[13]], margin = FALSE)
```

```{r}
levelplot(lv_8_01[[51]][[13]], margin = FALSE)
```

```{r}
levelplot(lv_4_01[[3]][[19]], margin = FALSE)
```
```{r}
levelplot(lv_4_01[[3]][[13]], margin = FALSE)
```

```{r}
levelplot(lv_4_01[[4]][[13]], margin = FALSE)
```




## Disturbance variables
```{r source landscape_variables}
#source(file = "R/04_disturbance_variables.R")
```


```{r load disturbance variables}
load(file = "output/RData/04_disturbance_variables.RData")
```

Logging history
```{r plot logging history s1}
lp(stack(dv_1_01[[1]][[1]], dv_1_01[[51]][[1]]))
```

```{r plot logging history s1}
lp(stack(dv_8_01[[1]][[1]], dv_8_01[[51]][[1]]))
```

```{r}
lp(stack(dv_8_01[[1]][[2]], dv_8_01[[51]][[2]]))
```
```{r}
lp(stack(dv_8_01[[1]][[3]], dv_8_01[[51]][[3]]))
```

```{r}
lp(stack(dv_8_01[[1]][[4]], dv_8_01[[51]][[4]]))
```

## Geoophysical variables
```{r source geophysical variables}
#source(file = "R/05_geophysical_variables.R")
```

```{r load geophysicial variables}
load(file = "output/RData/05_geophys_vars.RData")
```

## Climatic variables
```{r source climate variables}
source(file = "R/06_climate_variables.R")
```

```{r load climate variables}
load(flie = "output/RData/06_climate_variables.RData")
```


*pseudocode to fix things together later*
```{r}
mapply(lv, dv, FUN = stack)
```


# Distribution modelling

# Population viability analysis 








