---
title: "Forest Futures Analysis"
output: html_notebook:
  toc: true
  toc_depth: 3
author: GE Ryan
date: 20190827
---

# Setup and data preparation

## Controls and software

### Packages

Includes packages from github (development version or packages not on CRAN):

-  `steps`. Install with `remotes::install_github("steps-dev/steps")`
-  `metacapa`. Install with `remotes::install_github("mstrimas/metacapa")`

```{r packages}
library(dismo)
library(doMC)
library(dplyr)
library(foreach)
library(future)
library(future.apply)
library(gbm)
library(ggplot2)
library(lubridate)
library(lwgeom)
library(magrittr)
library(metacapa)
library(purrr)
library(raster)
library(rasterVis)
library(readr)
library(readxl)
library(rerddap)
library(rgdal)
library(rlang)
library(sf)
library(steps)
library(tibble)
library(tidyr)
library(viridis)
```

```{r load everything}
load(file = "output/RData/00_controls.RData")
load(file = "output/RData/01_landscape_variables.RData")
load(file = "output/RData/02_species_occurrences.RData")
load(file = "output/RData/03_LANDIS_variables.RData")
load(file = "output/RData/04_disturbance_variables.RData")
#load(file = "output/RData/04.01_aggregated_disturbance.RData")
load(file = "output/RData/05_geophys_vars.RData")
load(file = "output/RData/06_climate_variables.RData")
load(file = "output/RData/07_combined_variables.RData")
load(file = "output/RData/08_distribution_model_data.RData")
load(file = "output/RData/09_fit_distribution_models.RData")
load(file = "output/RData/10_predict_SDMs.RData")
load(file = "output/RData/10.1_preds_agg.RData")
load(file = "output/RData/11_pvas.RData")
load(file = "output/RData/11.1_pvas_lb.RData")
#load(file = "output/RData/11.1_pvas_gg_RData")
load(file = "output/RData/12_pva_pops.RData")
#load(file = "output/RData/12_pva_pops_supp.RData")

load(file = "output/RData/a_landis_output.RData")
```


### Functions
```{r source all functions}
source(file = "R/functions/source.functions.R")
source.functions("R/functions")
```


### Paths
```{r proj_paths}
proj_path <- "/home/unimelb.edu.au/ryange/rfst"
# proj_path <- "D:/Users/ryan/Dropbox/Work/RFA_STEPS/rfst/"
```

### Start year
```{r year0}
year0 <- 2019
```

### Timesteps
```{r ntimesteps}
ntimesteps <- 50
```

### Cores to use
```{r ncores}
ncores <- 20
```

### Simulation replicates
```{r nreplicates}
nreplicates <- 100
```


### LANDIS scenarios
```{r LANDIS scenarios}
scn_list <- c("1", "4", "8")
rep_list <- sprintf("%02d", 1:10)
```


```{r}

```


### Save computing controls
```{r save computing controls}
save(proj_path,
     year0,
     ntimesteps,
     ncores,
     nreplicates,
     scn_list,
     rep_list,
     source.functions,
     file = "output/RData/00_comp_controls.RData")
```


### Image controls

#### Png controls
```{r png controls}
res <- 600
width.png <- 3200
height.png <- 2000
```


## Landscape
```{r source landscape}
#source(file = "R/01_landscape_variables.R")
```

```{r load landscape vars}
load(file = "output/RData/01_landscape_variables.RData")
```

Mask of central highlands
```{r plot ch_mask}
lp(ch_mask)
```
LANDIS Ecoregions
```{r plot ch_eco}
lp(ch_eco)
```
Fire ecoregions
```{r plot ch_fire_eco}
lp(ch_fire_eco)
```
LANDIS initial conditions
```{r plot ch_ic}
lp(ch_ic)
```
Management zones
```{r plot ch_mgt}
lp(ch_mgt)
```
Aspect
```{r plot ch_aspect}
lp(ch_aspect)
```
Slope
```{r plot ch_slope}
lp(ch_slope)
```
Stand classifications
```{r plot ch_stands}
lp(ch_stands)
```
Fire history
```{r plot ch_fire_history}
lp(ch_fire_history)
```

Logging history
```{r plot logging history}
lp(ch_logging_history)
```


## Species occurrences

```{r source species occurrences}
#source(file = "R/02_species_occurrence.R")
```

```{r load species occurrences}
load(file = "output/RData/02_species_occurrences.RData")
```

```{r plot pa_lb_09}
ggplot() +
  geom_sf(data = ch_rfa) +
  geom_sf(data = pa_lb_09, aes(col = as.factor(PA), alpha = date))
```

```{r plot pa_lb_80}
ggplot() +
  geom_sf(data = ch_rfa) +
  geom_sf(data = pa_lb_80, aes(col = as.factor(PA), alpha = date))
```

```{r plot pa_gg_09}
ggplot() +
  geom_sf(data = ch_rfa) +
  geom_sf(data = pa_gg_09, aes(col = as.factor(PA), alpha = date))
```

```{r plot pa_gg_80}
ggplot() +
  geom_sf(data = ch_rfa) +
  geom_sf(data = pa_gg_80, aes(col = as.factor(PA), alpha = date))
```

## LANDIS outputs
```{r source LANDIS variables}
#source(file = "R/03_LANDIS_variables.R")
```

```{r load LANDIS variables}
load(file = "output/RData/03_LANDIS_variables.RData")
```

### Scenario 1: BAU: Timber harvesting, planned burning, climate change RCP 4.5
```{r}
lp(lv_1_01[[1]])
```
```{r}
levelplot(lv_1_01[[1]][[1]], margin = FALSE)
```

```{r}
levelplot(lv_1_01[[1]][[15]], margin = FALSE)
```

```{r}
levelplot(lv_1_01[[1]][[20]], margin = FALSE)
```
```{r}
levelplot(lv_1_01[[1]][[13]], margin = FALSE)
```

```{r}
levelplot(lv_1_01[[51]][[13]], margin = FALSE)
```

```{r}
levelplot(lv_4_01[[51]][[13]], margin = FALSE)
```

```{r}
levelplot(lv_8_01[[51]][[13]], margin = FALSE)
```

```{r}
levelplot(lv_4_01[[3]][[19]], margin = FALSE)
```
```{r}
levelplot(lv_4_01[[3]][[13]], margin = FALSE)
```

```{r}
levelplot(lv_4_01[[4]][[13]], margin = FALSE)
```




## Disturbance variables
```{r source landscape_variables}
#source(file = "R/04_disturbance_variables.R")
```


```{r load disturbance variables}
load(file = "output/RData/04_disturbance_variables.RData")
```

Logging history
```{r plot logging history s1}
lp(stack(dv_1_01[[1]][[6]], dv_1_01[[51]][[6]]))
```

```{r plot logging history s1}
lp(stack(dv_8_01[[1]][[4]], dv_8_01[[51]][[4]]))
```

```{r}
lp(stack(dv_8_01[[1]][[2]], dv_8_01[[51]][[2]]))
```
```{r}
lp(stack(dv_8_01[[1]][[3]], dv_8_01[[51]][[3]]))
```

```{r}
lp(stack(dv_8_01[[1]][[4]], dv_8_01[[51]][[4]]))
```



## Geoophysical variables
```{r source geophysical variables}
#source(file = "R/05_geophysical_variables.R")
```

```{r load geophysicial variables}
load(file = "output/RData/05_geophys_vars.RData")
```

## Climatic variables
```{r source climate variables}
source(file = "R/06_climate_variables.R")
```

```{r load climate variables}
load(file = "output/RData/06_climate_variables.RData")
```


## 07 Combined variables
```{r source combined variables}
#source(file = "R/07_combined_variables.R")
```


```{r load combined variables}
load(file = "output/RData/07_combined_variables.RData")
```
## 08 Distribution model data
```{r source distrinbution model data}
#source(file = "R/08_distribution_model_data.R")
```

```{r load distribution model data}
load(file = "output/RData/08_distribution_model_data.RData")
```



# Distribution modelling

## Fit models 
```{r source fit distribution models}
#source(file = "R/09_fit_distribution_models.R")
```


```{r load fit distribution models}
load(file = "output/RData/09_fit_distribution_models.RData")
```

## Predict to future

```{r source predict_SDMs}
#source(file = "R/10_predict_SDMs.R")
```

```{r load predict_SDMs}
load(file = "output/RData/10_predict_SDMs.RData")
```

# Population Viability Analyses

## 


```{r}
ggplot(pops, aes(x = scenario, y = emp)) +
  geom_boxplot() +
  geom_point(aes(colour = rep), position = position_jitter(width = 0.1, height = 0)) +
  facet_grid(species~., scales = "free")
  
```

```{r}
ggplot(pops.all, aes(x = rep, y = min.pop)) +
  geom_boxplot(aes(col = scenario)) +
  facet_grid(species~., scales = "free")

```

```{r}
ggplot(pops, aes(x = scenario, y = pr.ex)) +
  geom_boxplot() +
  geom_point(aes(colour = rep), position = position_jitter(width = 0.1, height = 0)) +
  facet_grid(species~., scales = "free")
```


```{r}
ggplot(pops, aes(x = scenario, y = mmp)) +
  geom_boxplot() +
  geom_point(aes(colour = rep), position = position_jitter(width = 0.1, height = 0)) +
  facet_grid(species~., scales = "free")
```


```{r}
zz <- simulation(
  landscape = set_gg$lsc[[1]],
  population_dynamics = set_gg$pd[[1]],
  timesteps = 50,
  replicates = 10
)
```

```{r}
qq <- simulation(
  landscape = simset_lb$lsc[[1]],
  population_dynamics = simset_lb$pd[[1]],
  timesteps = 10,
  replicates = 1
)
```
```{r}
sims_table <- expand.grid(
  scenario = scn_list,
  rep = rep_list
) %>%
  as_tibble %>%
  rowwise %>%
  mutate(
    dv = map(
      .f = get,
      .x = sprintf(
        "dv_%s_%s",
        scenario,
        rep
      )
    )
  )%>%
  ungroup %>%
  mutate(
    fi = map(
      .f = lapply,
      .x = dv,
      FUN = function(x){x[["fi"]]}
    ),
    fi  = map(
      
      .f = stack,
      .x = fi
     )
  ) %>%
  mutate(
    fi.sum = map(
      .f = function(x){
        sum(getValues(x), na.rm = TRUE)
      },
      .x = fi
    )
  ) %>%
  mutate(
    fi.sum = unnest(fi.sum)
  )

sims_table
```
```{r}
aa <- sims_table %>%
  mutate(
    fi.sum = map(
      .f = function(x){
        sum(getValues(x), na.rm = TRUE)
      },
      .x = fi
    )#,
    #fi.sum = unlist(fi.sum)
  )
```

```{r}
ggplot(sims_table, aes(x = scenario, y = fi.sum)) +
 geom_boxplot() +
  geom_point(aes(colour = rep), position = position_jitter(width = 0.1, height = 0))  
```


```{r}
tibble(price = c(
  114,
  310,
  
),
year = c(
  1988,
  1998,
  
))
```


```{r}
plot(brt_gg$init.pred[[25]], zlim = c(0,1))
plot(pa_gg_80b, add = TRUE)
```

```{r}
plot(brt_gg$init.pred[[11]], zlim = c(0,1))
plot(pa_gg_09x, add = TRUE)
```

```{r}
plot(brt_gg$init.pred[[11]], zlim = c(0,1))
plot(pa_gg_09b, add = TRUE)
```

```{r}
plot(brt_gg$init.pred[[11]], zlim = c(0,1))
plot(pa_gg_09bb, add = TRUE)
```


```{r}
ls()[grep("^dv_", ls())]
```

```{r}
fire_example <- expand.grid(
  scenario = scn_list,
  rep = rep_list
) %>%
  as_tibble %>%
  mutate(
    scn_id = paste0(scenario, "_", rep),
    dvid = paste0("dv_", scn_id)
  ) %>%
  rowwise %>%
  mutate(
    dv = map(
      .x = dvid,
      .f = get
    )
  ) %>%
  ungroup %>%
  mutate(
    fi = map(
      .x = dv,
      .f = function(x){
        y <- lapply(X = x, function(z){z[["fi"]]})
        
        y <- stack(y)
        
        return(y)
      }
    )
  ) %>%
  mutate(
    fi.50 = map(
      .x = fi,
      .f = ~.x[[50]]
    )
  )

fire_example

firestack <- stack(fire_example$fi.50)
```


```{r}
pm <- preds_lb_agg$predmaps[[1]]


pm <- patmat(
  x = pm,
  threshold = threshold_lb,
  out_path = "output/patch_matrix/",
  scn_id = "1_01",
  varset = "",
  species = "lb"
)

pm
```

```{r}
firech <- read_sf("data/shapefiles/DELWP_2019_interim_fire/FIRE_HISTOY_VICGRID_updated.shp") %>%
  st_transform(crs = ch_proj) %>%
  st_make_valid %>%
  st_crop(y = st_bbox(ch_mask))
```
```{r}
seasons <- unique(firech$season)[order(unique(firech$season))]

firelist <- lapply(
  X = seasons,
  FUN = function(seasons, data, mask){
    result <-  data %>% 
      filter(
        season == seasons
      ) %>%
      rasterize(
        y = mask,
        field = "season",
        fun = max,
        background = NA
      )
    
    return(result)
  },
  data = firech,
  mask = ch_mask
)

```

```{r}
filist <- lapply(
  X = firelist,
  FUN = function(x){
    x[!is.na(x)] <- 1
    return(x)
  }
)
```


```{r}
ch_fire_history <- read_sf("data/shapefiles/DELWP_2019_interim_fire/FIRE_HISTOY_VICGRID_updated.shp") %>%
  st_transform(crs = ch_proj) %>%
  st_make_valid %>%
  st_crop(y = st_bbox(ch_mask)) %>%
  rasterize(y = ch_mask, field = "season", fun = max, background = NA) %>%
  mask(mask = ch_mask, filename = "output/landscape_vars/fire_history.grd", overwrite = TRUE)

```

