---
title: "Illustrative Results for Leadbeater's Possum"
output: word_document
author: GE Ryan
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(include = FALSE)
```

# Derived variables

# Species distribution model

### Business as usual
```{r sdm 1_01 bau}
pgg_1_01 <- preds_gg_agg$predmaps[[1]][[c(1,11,21,31,41,51)]]

names(pgg_1_01) <- sprintf("sdm_20%s9", 1:6)

lp(pgg_1_01)
```

### No harvest after 30 years
```{r sdm 8_01 h30}
pgg_8_01 <- preds_gg_agg$predmaps[[3]][[c(1,11,21,31,41,51)]]

names(pgg_8_01) <- sprintf("sdm_20%s9", 1:6)

lp(pgg_8_01)
```
### No harvest
```{r sdm 4_01 nth}
pgg_4_01 <- preds_gg_agg$predmaps[[2]][[c(1,11,21,31,41,51)]]

names(pgg_4_01) <- sprintf("sdm_20%s9", 1:6)

lp(pgg_4_01)
```




# PVAs

## All stages

### Business as usual
```{r pop all stages 1_01 bau}
psr(simset_gg$pva_pops[[1]])
```

### No harvest after 30 years
```{r pop all stages 8_01 h30}
psr(simset_gg$pva_pops[[2]])
```

### No harvest
```{r pop all stages 4_01 nth}
psr(simset_gg$pva_pops[[3]])
```

## Total population

### Business as usual
```{r pop total 1_01 bau}
psr(simset_gg$pva_pops[[1]], stages = 0)
```

### No harvest after 30 years
```{r pop total 8_01 h30}
psr(simset_gg$pva_pops[[2]], stages = 0)
```

### No harvest
```{r pop total 4_01 nth}
psr(simset_gg$pva_pops[[3]], stages = 0)
```

## Spatial population

### Business as usual
```{r spat pop adult 1_01 bau}
psr_raster(simset_gg$pva_sims[[1]], timesteps = c(1,10,20,30,40,50))
```

### No harvest after 30 years
```{r spat pop adult 8_01 h30}
psr_raster(simset_gg$pva_sims[[2]], timesteps = c(1,10,20,30,40,50))
```

### No harvest
```{r spat pop adult 4_01 nth}
psr_raster(simset_gg$pva_sims[[3]], timesteps = c(1,10,20,30,40,50))
```

##



##############################################

### Business as usual
```{r 1_01 bau}

```

### No harvest after 30 years
```{r 8_01 h30}

```

### No harvest
```{r 4_01 nth}

```
