---
title: Illustrative Results of STEPS Population Viability Analysis for Leadbeater's
  Possum and Greater Glider
author: "GE Ryan - University of Melbourne"
output:
  word_document:
    toc: yes
    toc_depth: '3'
  pdf_document:
    fig_height: 6
    fig_width: 7
    fig_caption: true
    toc: yes
    toc_depth: 3
    includes:  
      in_header: header.tex
---

# Introduction

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
source("R/spartan/spartan_settings.R")
```

```{r}
.libPaths("/data/gpfs/projects/punim0995/gr_lib")
```

```{r packages, results = 'hide', warning = FALSE, include = FALSE}
library(magrittr)
library(dplyr)
library(tibble)
library(sf)
library(lwgeom)
library(rgdal)
library(readr)
library(readxl)
library(ggplot2)
library(lubridate)
library(foreach)
library(doMC)
library(future)
library(future.apply)
library(tidyr)
library(gbm)
library(dismo)
library(steps)
library(raster)
library(rasterVis)
library(rlang)
library(viridis)
library(purrr)
library(rerddap)
library(knitr)
```

```{r load everything}
load(file = "output/RData/00_controls.RData")
load(file = "output/RData/01_landscape_variables.RData")
load(file = "output/RData/02_species_occurrences.RData")
load(file = "output/RData/03_LANDIS_variables.RData")
load(file = "output/RData/04_disturbance_variables.RData")
load(file = "output/RData/04.2_temporally_agg_dist_vars.RData")
load(file = "output/RData/05_geophys_vars.RData")
load(file = "output/RData/06_climate_variables.RData")
#load(file = "output/RData/07_combined_variables.RData")
load(file = "output/RData/09_fit_distribution_models.RData")
load(file = "output/RData/10_predict_SDMs_agg.RData")
load(file = "output/RData/11_pva.RData")
#load(file = "output/RData/13.1a_mpc_all.RData")
```

```{r source all functions}
source(file = "R/functions/source.functions.R")
source.functions("R/functions")
```


# LANDIS results

## Maximum age
Maximum age in years of any tree in 1 ha cell - direct output from LANDIS.

Large image is 2019, multi-plots are 10 year time-slices.

### Business as usual

```{r max_age 1_01 bau, fig.cap = "Maximum age, business as usual scenario, 2019"}
max_age_1_01 <- lxtract(
  x = disturbance_variables$landis_vars[[1]][c(1,11,21,31,41,51)],
  y = "max_age",
  layernames = sprintf("max_age_20%s9", 1:6)
)
```

```{r, fig.cap = "Maximum age, no harvest scenario, 2019"}
lp(max_age_1_01, mm = 1)
```

```{r, fig.cap = "Maximum age, business as usual scenario, 2069"}
lp(max_age_1_01, mm = 6)
```

```{r, fig.cap = "Maximum age, business as usual scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(max_age_1_01)
```

### No harvest after 30 years
```{r max_age 8_01 h30}
max_age_8_01 <- lxtract(
  x = disturbance_variables$landis_vars[[11]][c(1,11,21,31,41,51)],
  y = "max_age",
  layernames = sprintf("max_age_20%s9", 1:6)
)
```

```{r fig.cap = "Maximum age, no harvest after 30 years scenario, 2019"}
lp(max_age_8_01, mm = 1)
```

```{r, fig.cap = "Maximum age, no harvest after 30 years scenario, 2069"}
lp(max_age_8_01, mm = 6)
```

```{r, fig.cap = "Maximum age, no harvest after 30 years scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(max_age_8_01)
```

### No harvest
```{r max_age 4_01 nth}
max_age_4_01 <- lxtract(
  x = disturbance_variables$landis_vars[[31]][c(1,11,21,31,41,51)],
  y = "max_age",
  layernames = sprintf("max_age_20%s9", 1:6)
)
```

```{r, fig.cap = "Maximum age, no harvest scenario, 2019"}
lp(max_age_4_01, mm = 1)
```

```{r, fig.cap = "Maximum age, no harvest scenario, 2069"}
lp(max_age_4_01, mm = 6)
```

```{r, fig.cap = "Maximum age, no harvest scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(max_age_4_01)
```

## Old growth eucalypt biomass
Average biomass of old-growth eucalypt forest - trees >150 years of age - in 1km radius.

Single plot is 2019, multi-plots are 10 year time-slices.

### Business as usual
```{r biom_oge_1k 1_01 bau}
biom_oge_1k_1_01 <- lxtract(
  x = disturbance_variables$landis_vars[[1]][c(1,11,21,31,41,51)],
  y = "biom_oge_1k",
  layernames = sprintf("OGbiom_20%s9", 1:6)
)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, business as usual scenario, 2019"}
lp(biom_oge_1k_1_01, mm = 1)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, business as usual scenario, 2069"}
lp(biom_oge_1k_1_01, mm = 6)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, business as usual scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(biom_oge_1k_1_01)
```

### No harvest after 30 years
```{r biom_oge_1k 8_01 h30}
biom_oge_1k_8_01 <- lxtract(
  x = disturbance_variables$landis_vars[[11]][c(1,11,21,31,41,51)],
  y = "biom_oge_1k",
  layernames = sprintf("OGbiom_20%s9", 1:6)
)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, no harvest after 30 years scenario, 2019"}
lp(biom_oge_1k_8_01, mm = 1)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, no harvest after 30 years scenario, 2069"}
lp(biom_oge_1k_8_01, mm = 6)
```


```{r fig.cap = "Average biomass of old growth eucalypts in 1 km radius, no harvest after 30 years scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(biom_oge_1k_8_01)
```

### No harvest
```{r biom_oge_1k 4_01 nth}
biom_oge_1k_4_01 <- lxtract(
  x = disturbance_variables$landis_vars[[31]][c(1,11,21,31,41,51)],
  y = "biom_oge_1k",
  layernames = sprintf("OGbiom_20%s9", 1:6)
)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, no harvest scenario, 2019"}
lp(biom_oge_1k_4_01, mm = 1)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, no harvest scenario, 2069"}
lp(biom_oge_1k_4_01, mm = 6)
```

```{r, fig.cap = "Average biomass of old growth eucalypts in 1 km radius, no harvest scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(biom_oge_1k_4_01)
```

## Acacia and midstorey biomass
Biomass of midstorey species and acacias important for Leadbeater's Possum.

### Business as usual
```{r lbm_biom 1_01 bau}
lbm_biom_1_01 <- lxtract(
  x = disturbance_variables$landis_vars[[1]][c(1,11,21,31,41,51)],
  y = "lbm_biom",
  layernames = sprintf("lbm_biom_20%s9", 1:6)
)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, business as usual scenario, 2019"}
lp(lbm_biom_1_01, mm = 1)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, business as usual scenario, 2069"}
lp(lbm_biom_1_01, mm = 6)
```

```{r,   fig.cap = "Biomass of acacias and midstorey species, business as usual scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(lbm_biom_1_01)
```

### No harvest after 30 years
```{r lbm_biom 8_01 h30}
lbm_biom_8_01 <- lxtract(
  x = disturbance_variables$landis_vars[[11]][c(1,11,21,31,41,51)],
  y = "lbm_biom",
  layernames = sprintf("lbm_biom_20%s9", 1:6)
)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, no harvest after 30 years scenario, 2019"}
lp(lbm_biom_8_01, mm = 1)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, no harvest after 30 years scenario, 2069"}
lp(lbm_biom_8_01, mm = 6)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, no harvest after 30 years scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(lbm_biom_8_01)
```


### No harvest
```{r lbm_biom 4_01 nth}
lbm_biom_4_01 <- lxtract(
  x = disturbance_variables$landis_vars[[31]][c(1,11,21,31,41,51)],
  y = "lbm_biom",
  layernames = sprintf("lbm_biom_20%s9", 1:6)
)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, no harvest scenario, 2019"}
lp(lbm_biom_4_01, mm = 1)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, no harvest scenario, 2069"}
lp(lbm_biom_4_01, mm = 6)
```

```{r, fig.cap = "Biomass of acacias and midstorey species, no harvest scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(lbm_biom_4_01)
```


# Disturbances

## Fires
Cells where fires occured over 10 year period, with large map showing 2019-2028, and multi-plot showing all following periods of 10 years.

Fires are stochasticaly generated based on fire weather and fuel loads in the simulated landscape, and each simulation has unique fire outcomes.

### Business as usual
```{r fire_1_01 bau, fig.cap = "Fires over 10 year period business as usual scenario, 2019-2028"}
lp(temporally_agg_dist_vars$fire_ag[[31]][[1]], twocol = TRUE)
```

```{r, fig.cap = "Fires over 10 year period business as usual scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(temporally_agg_dist_vars$fire_ag[[31]], twocol = TRUE)
```

### No harvest after 30 years
```{r fire_8_01 h30, fig.cap = "Fires over 10 year period no harvest after 30 years scenario, 2019-2028"}
lp(temporally_agg_dist_vars$fire_ag[[41]][[1]], twocol = TRUE)
```

```{r, fig.cap = "Fires over 10 year period no harvest after 30 years scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(temporally_agg_dist_vars$fire_ag[[41]], twocol = TRUE)
```

### No harvest
```{r fire_4_01 nth, fig.cap = "Fires over 10 year period no harvest scenario, 2019-2028"}
lp(temporally_agg_dist_vars$fire_ag[[11]][[1]], twocol = TRUE)
```

```{r, fig.cap = "Fires over 10 year period no harvest scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(temporally_agg_dist_vars$fire_ag[[11]], twocol = TRUE)
```

### Fires in time 50 (2068) in each LANDIS run
Fires in year 50 of all 30 LANDIS simulations (10 runs of each of the three scenarios) - illustratiing variation in fire occurrence in a single simulated timestep among simulations.

```{r}
fire_example <- disturbance_variables %>%
  mutate(
    fi = map(
      .x = dist_vars,
      .f = function(x){
        y <- lapply(X = x, function(z){z[["fi"]]})
        
        y <- stack(y)
        
        return(y)
      }
    )
  ) %>%
  mutate(
    fi.50 = map(
      .x = fi,
      .f = ~.x[[50]]
    )
  ) %>%
  arrange(scenario)
 
firestack <- stack(fire_example$fi.50)
```

#### Business as usual
```{r, fig.cap = "Fires in 2068, business as usual scenario, simulations 1-6"}
lp(firestack[[1:6]], twocol = TRUE)
```

```{r, fig.cap = "Fires in 2068, business as usual scenario, simulations 7-10"}
lp(firestack[[7:10]], twocol = TRUE)
```

#### No harvest after 30 years
```{r, fig.cap = "Fires in 2068, no harvest after 30 years scenario , simulations 1-6"}
lp(firestack[[21:26]], twocol = TRUE)
```

```{r, fig.cap = "Fires in 2068, no harvest after 30 years scenario, simulations 7-10"}
lp(firestack[[27:30]], twocol = TRUE)
```

#### No harvest
```{r , fig.cap = "Fires in 2068, no harvest scenario, simulations 1-6"}
lp(firestack[[11:16]], twocol = TRUE)
```

```{r, fig.cap = "Fires in 2068, no harvest scenario, simulations 7-10"}
lp(firestack[[17:20]], twocol = TRUE)
```


## Timber harvest
Areas harvested in a 10 year period. Large image is 2019-2028, multi-plot is over all 10 year periods.

### Business as usual
```{r harvest_1_01 bau, fig.cap = "Timber harvest over 10 year period business as usual scenario, 2019-2028"}
lp(temporally_agg_dist_vars$harvest_ag[[31]][[1]], twocol = TRUE)
```

```{r, fig.cap = "Timber harvest over 10 year period business as usual scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(temporally_agg_dist_vars$harvest_ag[[31]], twocol = TRUE)
```

### No harvest after 30 years
```{r harvest_8_01 h30, fig.cap = "Timber harvest over 10 year period no harvest after 30 years scenario, 2019-2028"}
lp(temporally_agg_dist_vars$harvest_ag[[41]][[1]], twocol = TRUE)
```

```{r, fig.cap = "Timber harvest over 10 year period no harvest after 30 years scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(temporally_agg_dist_vars$harvest_ag[[41]], twocol = TRUE)
```

### No harvest
```{r harvest_4_01 nth, fig.cap = "Timber harvest over 10 year period no harvest scenario, 2019-2028"}
lp(temporally_agg_dist_vars$harvest_ag[[11]][[1]], twocol = TRUE)
```

```{r, fig.cap = "Timber harvest over 10 year period no harvest scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(temporally_agg_dist_vars$harvest_ag[[11]], twocol = TRUE)
```


## Planned burning
Areas burnt through planned burning in a 10 year period. Large image is 2019-2028, multi-plot is over all 10 year periods.

### Business as usual
```{r pb_1_01 bau, fig.cap = "Planned burning over 10 year period business as usual scenario, 2019-2028"}
lp(temporally_agg_dist_vars$pb_ag[[31]][[1]], twocol = TRUE)
```

```{r, fig.cap = "Planned burning over 10 year period business as usual scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(temporally_agg_dist_vars$fire_ag[[31]], twocol = TRUE)
```

### No harvest after 30 years
```{r pb_8_01 h30, fig.cap = "Planned burning over 10 year period no harvest after 30 years scenario, 2019-2028"}
lp(temporally_agg_dist_vars$fire_ag[[41]][[1]], twocol = TRUE)
```

```{r, fig.cap = "Planned burning over 10 year period no harvest after 30 years scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(temporally_agg_dist_vars$fire_ag[[41]], twocol = TRUE)
```

### No harvest
```{r pb_4_01 nth, fig.cap = "Planned burning over 10 year period no harvest scenario, 2019-2028"}
lp(temporally_agg_dist_vars$fire_ag[[11]][[1]], twocol = TRUE)
```

```{r, fig.cap = "Planned burning over 10 year period no harvest scenario, 2019-2028, 2029-2038, 2039-2048, 2049-2058, 2059-2068"}
lp(temporally_agg_dist_vars$fire_ag[[11]][[1]], twocol = TRUE)
```

## Total burnt and harvested
```{r, cache = TRUE}
# sims_table <-  disturbance_variables %>%
#   mutate(
#     fi = map(
#       .f = lapply,
#       .x = dist_vars,
#       FUN = function(x){x[["fi"]]}
#     ),
#     fi  = map(
#       
#       .f = stack,
#       .x = fi
#      )
#   )
# 
# 
# sims_table <- sims_table %>%
#   mutate(
#     fi.sum = map(
#       .f = function(x){
#         sum(getValues(x), na.rm = TRUE)
#       },
#       .x = fi
#     )
#   )
# 
# 
# sims_table <- unnest(sims_table, cols = fi.sum) %>%
#   mutate(
#     scenario = case_when(scenario == "TH19_rcp45_PB" ~ "BAU",
#                          scenario == "TH30_rcp45_PB" ~ "No harvest",
#                          scenario == "TH00_rcp45_PB" ~ "Cease harvest Y30")
#   )
# 
# 
# sims_table <- sims_table %>%
#   mutate(
#     lo = map(
#       .f = lapply,
#       .x = dist_vars,
#       FUN = function(x){x[["lo"]]}
#     ),
#     lo  = map(
#       
#       .f = stack,
#       .x = lo
#      )
#   )
# 
# 
# sims_table <- sims_table %>%
#   mutate(
#     lo.sum = map(
#       .f = function(x){
#         sum(getValues(x), na.rm = TRUE)
#       },
#       .x = lo
#     )
#   )
# 
# sims_table <- unnest(sims_table, cols = lo.sum)
```

```{r, fig.cap="Total area burnt in each LANDIS simulation, by scenario type."}
# ggplot(sims_table, aes(x = scenario, y = fi.sum)) +
#   geom_boxplot() +
#   geom_point(aes(colour = scenario_replicate), position = position_jitter(width = 0.1, height = 0)) 
```

```{r, fig.cap = "Total area harvested in each LANDIS simulation, by scenario type."}
# ggplot(sims_table, aes(x = scenario, y = lo.sum)) +
#   geom_boxplot() +
#   geom_point(aes(colour = scenario_replicate), position = position_jitter(width = 0.1, height = 0)) 
```

# Climate

## Precipitation

### January, RCP 4.5
Rainfall in January, large image is 2019, multi-plot shows 10 year time-slices.

```{r precipJan4.5}
precipJan4.5 <- lxtract(
  x =  clim_vars$climate_projections[[1]][c(1,11,21,31,41,51)],
  y = 1,
  layernames = sprintf("prec_djf_20%s9", 1:6)
)
```

```{r, fig.cap= "Rainfall, January, 2019"}
lp(precipJan4.5,
   mm = 1)
```

```{r, fig.cap = "Rainfall, January, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(precipJan4.5)
```

### July, RCP 4.5
Rainfall in July, large image is 2019, multi-plot shows 10 year time-slices.

```{r precipJul4.5}
precipJul4.5 <- lxtract(
  x =  clim_vars$climate_projections[[1]][c(1,11,21,31,41,51)],
  y = 2,
  layernames = sprintf("prec_jja_20%s9", 1:6)
)
```

```{r, fig.cap = "Rainfall, July, 2019"}
lp(precipJul4.5, mm = 6)
```

```{r, fig.cap= "Rainfall, July, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(precipJul4.5)
```


## Temperature

### January, maximum temperature, RCP 4.5
Large image is 2019, multi-plot shows 10 year time-slices.

```{r tmaxJan4.5}
tmaxJan4.5 <- lxtract(
  x =  clim_vars$climate_projections[[1]][c(1,11,21,31,41,51)],
  y = 3,
  layernames = sprintf("tmax_djf_20%s9", 1:6)
)
```

```{r, fig.cap = "Maximum temperature, January, 2019"}
lp(tmaxJan4.5, mm = 1)
```

```{r, fig.cap = "Maximum temperature, January, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(tmaxJan4.5)
```

### July, minumum temperature, RCP 4.5
Large image is 2019, multi-plot shows 10 year time-slices.

```{r tminJul4.5}
tminJul4.5 <- lxtract(
  x =  clim_vars$climate_projections[[1]][c(1,11,21,31,41,51)],
  y = 4,
  layernames = sprintf("tmin_jja_20%s9", 1:6)
)
```

```{r, fig.cap="Minimum temerature, July, 2019"}
lp(tminJul4.5, mm = 1)
```


```{r fig.cap="Minimum temperature, July, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(tminJul4.5)
```

# Leadbeater's Possum results

## Species distribution model

Summary information for Leadbeater's possum species distribution model.

Variables are, in order:

- maximum January temperature,
- January rainfall,
- maximum age of trees,
- log vertical distance from major waterways,
- July minimum temperature,
- proportion of midstorey biomass,
- total midstorey biomass,
- July rainfall,
- log vertical distance from minor waterways,
- proportion of biomass >150 years old,
- log vertical distance from salt waterway,
- anisotronic heating x ruggedness, thorium,
- log vertical distance from any waterway,
- proportion of old growth biomass in surrounding 3 ha x 3ha area,
- total biomass of old growth forest in surrounding 3 ha x 3 ha area 

```{r, fig.cap="Percentage contribution of Leadbeater's possum distribution model"}
summary(sdm_results$brt.fit[[1]])
```

```{r, fig.cap="Partial dependence plot for Leadbeater's possum species distribution model"}
gbm.plot(sdm_results$brt.fit[[1]])
```

```{r sdm 1_01 bau lb, fig.cap="Baseline species distribution model for Leadbeater's possum"}
plb_BAU <- pva_results_ch$aggmaps[[709]][[c(1,11,21,31,41,51)]]

names(plb_BAU) <- sprintf("sdm_20%s9", 1:6)

lp(plb_BAU[[1]])
```

```{r, fig.cap="Baseline species distribution model for Leadbeater's possum, with presence (yellow) and absence (blue) records overlaid"}
plot(plb_BAU[[1]], col = magma(16))
plot(pa_data$pa_dat[[1]][2], pch = 20, cex = 0.3,  add = TRUE)
```

### SDM spatial predictions

### Business as usual
```{r, fig.cap = "Species distribution model for Leadbeater's possum, business as usual scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(plb_BAU)
```

### No harvest after 30 years
```{r sdm 8_01 h30 lb, fig.cap = "Species distribution model for Leadbeater's possum, no harvest after 30 years scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
plb_NH30 <- pva_results_ch$aggmaps[[944]][[c(1,11,21,31,41,51)]]

names(plb_NH30) <- sprintf("sdm_20%s9", 1:6)

lp(plb_NH30[[1]])
```

### No harvest
```{r sdm 4_01 nth lb, fig.cap = "Species distribution model for Leadbeater's possum, no harvest scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
plb_NH <- pva_results_ch$aggmaps[[238]][[c(1,11,21,31,41,51)]]

names(plb_NH) <- sprintf("sdm_20%s9", 1:6)

lp(plb_NH[[1]])
```

## Population viability analysis

## All life stages
Population for each life history stage over 100 simulations for a single LANDIS simulation of each management scenario.

Coloured lines are mean, grey lines are population over a single simulation. Panels are newborn (left), juvenile (middle), and adult (right) populations.

### Business as usual
```{r pop all stages 1_01 bau lb, fig.cap = "Newborn, juvenile, and adult populations of Leadbeater's possum, business as usual scenario"}
psr(pva_results_ch$pva[[709]])
```

### No harvest after 30 years
```{r pop all stages 8_01 h30 lb, fig.cap = "Newborn, juvenile, and adult populations of Leadbeater's possum, no harvest after 30 years scenario"}
psr(pva_results_ch$pva[[944]])
```

### No harvest
```{r pop all stages 4_01 nth lb, fig.cap = "Newborn, juvenile, and adult populations of Leadbeater's possum, no harvest scenario"}
psr(pva_results_ch$pva[[238]])
```

## Total population

Total population for each of 100 PVA simulations for a single LANDIS simulation of each management scenario.

Dark grey line is mean, grey ribbon is 95% bound of simulated population size, and light grey lines are population over a single PVA simulation. Dotted line below is the expected minimum population size, which is red when it equals zero.

### Business as usual
```{r pop total 1_01 bau lb, fig.cap = "Total populationof Leadbeater's possum, business as usual scenario"}
psr(pva_results_ch$pva[[709]], stages = 0, ylim = c(0, 5000))
```

### No harvest after 30 years
```{r pop total 8_01 h30 lb, fig.cap = "Total populationof Leadbeater's possum, no harvest after 30 years scenario"}
psr(pva_results_ch$pva[[944]], stages = 0, ylim = c(0, 5000))
```

### No harvest
```{r pop total 4_01 nth lb, fig.cap = "Total populationof Leadbeater's possum, no harvest scenario"}
psr(pva_results_ch$pva[[238]], stages = 0, ylim = c(0, 5000))
```

## Spatial population
Population as distributed in space. First multi-plot is the initial population in each life-history stage, and second multi-plot is the simulated total population at 10-year time-slices.

### Business as usual
```{r, fig.cap = "Initial population of Leadbeater's possum, Business as usual scenario"}
#lp(simset_lb$init_pop[[1]])
```

```{r spat pop adult 1_01 bau lb, fig.cap = "Total population of Leadbeater's possum, business as usual scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
#psr_raster(simset_lb$pva_sims[[1]], timesteps = c(1,10,20,30,40,50))
```

### No harvest after 30 years
```{r, fig.cap = "Initial population of Leadbeater's possum, no harvest after 30 years scenario"}
#lp(simset_lb$init_pop[[2]])
```


```{r spat pop 8_01 h30 lb, fig.cap = "Total population of Leadbeater's possum, no harvest after 30 years scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
#psr_raster(simset_lb$pva_sims[[2]], timesteps = c(1,10,20,30,40,50))
```

### No harvest
```{r, fig.cap = "Initial population of Leadbeater's possum, no harvest scenario"}
#lp(simset_lb$init_pop[[3]])
```

```{r spat pop 4_01 nth lb, fig.cap = "Total population of Leadbeater's possum, no harvest scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
#psr_raster(simset_lb$pva_sims[[3]], timesteps = c(1,10,20,30,40,50))
```

# Greater Glider

## Species distribution model

Summary information for greater glider species distribution model.

Variables are, in order:

- maximum age of trees,
- January rainfall,
- July minimum temperature,
- July rainfall,
- thorium,
- log vertical distance from major waterways,
- anisotronic heating x ruggedness, thorium,
- biomass of greater glider food tree species,
- log vertical distance from minor waterways,
- log vertical distance from any waterway,
- proportion of biomass of greater glider food tree species,
- proportion of biomass >150 years old,
- proportion of old growth biomass in surrounding 1 km radius,
- biomass of old growth known greater glider den tree species,
- maximum January temperature,
- total old growth biomass in surrounding 1 km radius,
- log vertical distance from salt waterway,
- proportion biomass of old growth known greater glider den tree species.

```{r, fig.cap="Percentage contribution of greater glider distribution model"}
summary(sdm_results$brt.fit[[2]])
```

```{r, fig.cap="Partial dependence plot for greater glider species distribution model"}
gbm.plot(sdm_results$brt.fit[[2]])
```


```{r sdm 1_01 bau gg, fig.cap="Baseline species distribution model for greater glider"}
pgg_BAU <- pva_results_ch$aggmaps[[711]][[c(1,11,21,31,41,51)]]

names(pgg_BAU) <- sprintf("sdm_20%s9", 1:6)

lp(pgg_BAU[[1]])
```

```{r, fig.cap="Baseline species distribution model for greater glider, with presence (yellow) and absence (blue) records overlaid"}
plot(pgg_BAU[[1]], col = magma(16))
plot(pa_data$pa_dat[[2]][2], pch = 20, cex = 0.3,  add = TRUE)
```

### SDM spatial predictions

### Business as usual
```{r, fig.cap = "Species distribution model for greater glider, business as usual scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
lp(pgg_BAU)
```

### No harvest after 30 years
```{r sdm 8_01 h30 gg, fig.cap = "Species distribution model for greater glider, no harvest after 30 years scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
pgg_NH30 <- pva_results_ch$aggmaps[[946]][[c(1,11,21,31,41,51)]]

names(pgg_NH30) <- sprintf("sdm_20%s9", 1:6)

lp(pgg_NH30)
```

### No harvest
```{r sdm 4_01 nth gg, fig.cap = "Species distribution model for greater glider, no harvest scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
pgg_NH <- pva_results_ch$aggmaps[[240]][[c(1,11,21,31,41,51)]]

names(pgg_NH) <- sprintf("sdm_20%s9", 1:6)

lp(pgg_NH)
```


## Populaition viability analysis

## All life stages
Population for each life history stage over 100 simulations for a single LANDIS simulation of each management scenario.

Coloured lines are mean, grey lines are population over a single simulation. Panels are newborn (left), juvenile (middle), and adult (right) populations.

### Business as usual
```{r pop all stages 1_01 bau gg, fig.cap = "Newborn, juvenile, and adult populations of greater glider, business as usual scenario"}
psr(pva_results_ch$pva[[711]])
```

### No harvest after 30 years
```{r pop all stages 8_01 h30 gg, fig.cap = "Newborn, juvenile, and adult populations of greater glider, no harvest after 30 years scenario"}
psr(pva_results_ch$pva[[946]])
```

### No harvest
```{r pop all stages 4_01 nth gg, fig.cap = "Newborn, juvenile, and adult populations of greater glider, no harvest scenario"}
psr(pva_results_ch$pva[[240]])
```

## Total population

Total population for each of 100 PVA simulations for a single LANDIS simulation of each management scenario.

Dark grey line is mean, grey ribbon is 95% bound of simulated population size, and light grey lines are population over a single PVA simulation. Dotted line below is the expected minimum population size, which is red when it equals zero.

### Business as usual
```{r pop total 1_01 bau gg, fig.cap = "Total populationof greater glider, business as usual scenario"}
psr(pva_results_ch$pva[[711]], stages = 0, ylim = c(0, 10000))
```

### No harvest after 30 years
```{r pop total 8_01 h30 gg, fig.cap = "Total populationof greater glider, no harvest after 30 years scenario"}
psr(pva_results_ch$pva[[946]], stages = 0, ylim = c(0, 10000))
```

### No harvest
```{r pop total 4_01 nth gg, fig.cap = "Total populationof greater glider, no harvest scenario"}
psr(pva_results_ch$pva[[240]], stages = 0, ylim = c(0, 10000))
```

## Spatial population
Population as distributed in space. First multi-plot is the initial population in each life-history stage, and second multi-plot is the simulated total population at 10-year time-slices.

### Business as usual
```{r, fig.cap = "Initial population of greater glider, Business as usual scenario"}
#lp(simset_gg$init_pop[[1]])
```

```{r spat pop adult 1_01 bau gg, fig.cap = "Total population of greater glider, business as usual scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
#psr_raster(simset_gg$pva_sims[[1]], timesteps = c(1,10,20,30,40,50))
```

### No harvest after 30 years
```{r, fig.cap = "Initial population of greater glider, no harvest after 30 years scenario"}
#lp(simset_gg$init_pop[[2]])
```


```{r spat pop 8_01 h30 gg, fig.cap = "Total population of greater glider, no harvest after 30 years scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
#psr_raster(simset_gg$pva_sims[[2]], timesteps = c(1,10,20,30,40,50))
```

### No harvest
```{r, fig.cap = "Initial population of greater glider, no harvest scenario"}
#lp(simset_gg$init_pop[[3]])
```

```{r spat pop 4_01 nth gg, fig.cap = "Total population of greater glider, no harvest scenario, 2019, 2029, 2039, 2049, 2059, 2069"}
#psr_raster(simset_gg$pva_sims[[3]], timesteps = c(1,10,20,30,40,50))
```
