---
title: "Landacape variable projections"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, dpi = 300)
```

```{r}
source("R/spartan/spartan_settings.R")
```


```{r}
#.libPaths("/data/gpfs/projects/punim0995/gr_lib")
```

```{r}
library(raster)
library(dplyr)
library(purrr)
#library(tibble)
library(tidyr)
library(dismo)
library(gbm)
library(rasterVis)
```

```{r}
load(file = "output/RData/00_controls.RData")
load(file = "output/RData/01_landscape_variables.RData")
#load(file = "output/RData/02_species_occurrences.RData")
load(file = "output/RData/05_geophys_vars.RData")
load(file = "output/RData/07_combined_variables.RData")
#load(file = "output/RData/08_distribution_model_data.RData")
```

```{r}
source.functions("R/functions")
```

```{r}
#var_set
```


Maximum age
`max_age`
```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract("max_age") %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
```




Midstorey species - proportion of biomass
`lbm_prop`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract("lbm_prop") %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    zlim = c(0, 1),
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  
```

Midstorey species - total biomass
`lbm_biom`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract("lbm_biom") %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  
```

Acacia species - proportion of biomass
`ac_prop`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract("ac_prop") %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    zlim = c(0, 1),
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  
```

Acacia species - total biomass
`ac_prop`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract("ac_biom") %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  
```

Greater glider feed tree species - proportion of biomass
`ggf_prop`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract("ggf_prop") %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    zlim = c(0, 1),
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  
```

Greater glider feed tree species - total biomass
`ggf_biom`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract("ggf_biom") %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  
```

Greater glider den tree species >150 years old - proportion of biomass
`ggd_prop_og`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract("ggd_prop_og") %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    zlim = c(0, 1),
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  
```

Greater glider den tree species >150 years old - total biomass
`ggd_biom_og`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract("ggd_biom_og") %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  
```
Old growth Eucalypts (>150 years) - proportion of biomass
`prop_oge`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract("prop_oge") %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    zlim = c(0, 1),
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  
```

Old growth Eucalypts (>150 years) - mean proportion of biomass in 3x3 ha window
`prop_oge`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract("prop_oge_3h") %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    zlim = c(0, 1),
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  
```

Old growth Eucalypts (>150 years) - mean proportion of biomass in 1km radius window
`prop_oge`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract("prop_oge_1k") %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    zlim = c(0, 1),
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  
```


Old growth Eucalypts (>150 years) - biomass
`prop_oge`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract("biom_oge") %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  
```

Old growth Eucalypts (>150 years) - mean biomass in 3x3 ha window
`prop_oge`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract("biom_oge_3h") %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  


```

Summer rainfall (mm)
`prec_djf`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract(y =32 ) %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  
```

Winter rainfall (mm)
`prec_jja`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract(y = 33) %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  
```

Summer maximum temperature - mean (c)
`tmax_djf`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract(y = 34) %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
  
```

Winter minimum temperature - mean (c)
`prec_djf`

```{r}
var_set %>%
  filter(cscnid == "TH00_rcp45_PB_01_ACCESS1-0") %>%
  pull(all_vars) %>%
  .[[1]] %>%
  lxtract(y = 35) %>%
  .[[c(1, 10, 20, 30, 40, 50)]] %>%
  lp(
    names.attr = c(2019, 2029, 2039, 2049, 2059, 2069) %>% as.character
  )
```
Log-vertical distance from any waterway
`lvdaw`

```{r}
lp(geo_vars[["lvdaw"]])
```

Log-vertical distance from major waterway
`lvdma`

```{r}
lp(geo_vars[["lvdma"]])
```


Log-vertical distance from minor waterway
`lvdmi`

```{r}
lp(geo_vars[["lvdmi"]])
```

Log-vertical distance above saline waterway
`lvdsw`

```{r}
lp(geo_vars[["lvdsw"]])
```

Thorium

```{r}
lp(geo_vars[["tho"]])
```

Anisotronic heating x ruggedness

```{r}
lp(geo_vars[["ahr"]])
```

