---
title: "Presence-absence data from VBA for potential PVA species"
author: Gerry Ryan
date: September 16, 2019
output: html_document
---

```{r setup, echo = FALSE, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

```{r prelims, echo = FALSE, include = FALSE}
library(knitr)
library(dplyr)
library(sp)
library(sf)
library(readr)
library(readxl)
library(tidyr)
library(ggplot2)
library(lubridate)

load(file = "output/RData/00_controls.RData")
load(file = "output/RData/01_landscape_variables.RData")

source.functions("R/functions")
```

```{r eg_rfa, include = FALSE}
eg_rfa <- rfa[rfa$NAME== "EAST GIPPSLAND",] 

eg_rfa
```


Outlining VBA data available for potential PVA species.

Candidates:

* Broad-toothed rat
* Long-footed potoroo
* Sooty Owl
* Baw Baw frog

# Broad-toothed rat

### VBA data available
```{r br_all}
br_all <- proc.vba(x = "data/tabular/vba_Potorous_20200115.csv", project.crs = ch_proj, cutoff.date = "1700-01-01") %>%
  mutate(year = year(date),
         decade = year - (year %% 10)) %>%
  filter(species == "Potorous longipes")

br_all
```

### Table of presences and absences
```{r br presence-absence}
table(br_all$PA)
```
### PAs by decade
```{r br pa-decade}
table(br_all$decade, br_all$PA)
```
### Map of PAs with reference to RFA regions

```{r br map all rfa}
ggplot() +
  geom_sf(data = rfa) +
  geom_sf(data = br_all, aes(col = as.factor(decade), fill = as.factor(decade))) +
  scale_colour_viridis_d() +
  scale_fill_viridis_d() +
  guides(col = guide_legend(title = "Decade"), fill = guide_legend(title = "Decade"))
```

### And in the RFA regions of interest
```{r br rfa}
br_ch <- br_all[ch_rfa, ]
br_eg <- br_all[eg_rfa, ]
```

### PA records in the Central Highlands
```{r pa br_ch}
table(br_ch$PA)
```
### And East Gippsland
```{r ba br_eg}
table(br_eg$PA)
```

### And by decade...

### In the Central Highlands
```{r pa br_ch decade}
table(br_ch$decade, br_ch$PA)
```
### And East Gippsland
```{r pa br_eg decade}
table(br_eg$decade, br_eg$PA)
```

### Map of PAs in Central Highlands

```{r br map ch_rfa}
ggplot() +
  geom_sf(data = ch_rfa) +
  geom_sf(data = br_ch, aes(col = as.factor(decade), fill = as.factor(decade))) +
  scale_colour_viridis_d() +
  scale_fill_viridis_d() +
  guides(col = guide_legend(title = "Decade"), fill = guide_legend(title = "Decade"))
```

### And East Gippsland

```{r br map eg_rfa}
ggplot() +
  geom_sf(data = eg_rfa) +
  geom_sf(data = br_eg, aes(col = as.factor(decade), fill = as.factor(decade))) +
  scale_colour_viridis_d() +
  scale_fill_viridis_d() +
  guides(col = guide_legend(title = "Decade"), fill = guide_legend(title = "Decade"))
```
