---
title: "PVA Results Lace monitor"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r}
spti <- "Lace monitor"
spfil <- "vava"
```


```{r}
knitr::opts_chunk$set(fig.width=6, fig.height=8, echo = FALSE, message = FALSE)
```


```{r}
source("R/spartan/spartan_settings.R")
```


```{r}
library(magrittr)
library(tibble)
library(dplyr)
library(purrr)
library(tidyr)
library(raster)
library(sp)
library(sf)
library(ggplot2)
library(forcats)
library(patchwork)
library(cowplot)
```

```{r}
load(file = "output/RData/00_controls.RData")
load(file = "output/RData/11.4_pva_results.R")
```

```{r}
source.functions("R/functions")
```

```{r}
pvr_r <- pvr %>%
  filter(sp == spfil)
```


# Trajectory plots
```{r}
knitr::opts_chunk$set(fig.width=6, fig.height=4, echo = FALSE, message = FALSE)
```

### CH
No harvest no planned burning RCP4.5

```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH00_rcp45_NB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH00_rcp45_NB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH00_rcp45_NB_01_ACCESS1-0"
  ) %>%
  doccplot
```

No harvest RCP4.5  

```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH00_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH00_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH00_rcp45_PB_01_ACCESS1-0"
  ) %>%
  doccplot
```

Stop harvest 2030 RCP4.5 

```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH30_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH30_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH30_rcp45_PB_01_ACCESS1-0"
  ) %>%
  doccplot
```

Ongoing harvest RCP4.5
```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH19_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH19_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH19_rcp45_PB_01_ACCESS1-0"
  ) %>%
  doccplot
```

No harvest RCP8.5                   
```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH00_rcp85_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH00_rcp85_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH00_rcp45_PB_01_ACCESS1-0"
  ) %>%
  doccplot
```

Stop harvest 2030 RCP8.5            
```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH30_rcp85_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH30_rcp85_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "CH",
    cscnid == "TH30_rcp85_PB_01_ACCESS1-0"
  ) %>%
  doccplot
```


### EG19

No harvest no planned burning RCP4.5

```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH00_rcp45_NB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH00_rcp45_NB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH00_rcp45_NB_01_ACCESS1-0"
  ) %>%
  doccplot
```

No harvest RCP4.5  

```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH00_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH00_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH00_rcp45_PB_01_ACCESS1-0"
  ) %>%
  doccplot
```

Stop harvest 2030 RCP4.5 

```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH30_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH30_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH30_rcp45_PB_01_ACCESS1-0"
  ) %>%
  doccplot
```

Ongoing harvest RCP4.5
```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH19_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH19_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH19_rcp45_PB_01_ACCESS1-0"
  ) %>%
  doccplot
```

No harvest RCP8.5                   
```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH00_rcp85_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH00_rcp85_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH00_rcp45_PB_01_ACCESS1-0"
  ) %>%
  doccplot
```

Stop harvest 2030 RCP8.5            
```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH30_rcp85_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH30_rcp85_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG19",
    cscnid == "TH30_rcp85_PB_01_ACCESS1-0"
  ) %>%
  doccplot
```


### EG20

No harvest no planned burning RCP4.5

```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH00_rcp45_NB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH00_rcp45_NB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH00_rcp45_NB_01_ACCESS1-0"
  ) %>%
  doccplot
```

No harvest RCP4.5  

```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH00_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH00_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH00_rcp45_PB_01_ACCESS1-0"
  ) %>%
  doccplot
```

Stop harvest 2030 RCP4.5 

```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH30_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH30_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH30_rcp45_PB_01_ACCESS1-0"
  ) %>%
  doccplot
```

Ongoing harvest RCP4.5
```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH19_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH19_rcp45_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH19_rcp45_PB_01_ACCESS1-0"
  ) %>%
  doccplot
```

No harvest RCP8.5                   
```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH00_rcp85_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH00_rcp85_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH00_rcp45_PB_01_ACCESS1-0"
  ) %>%
  doccplot
```

Stop harvest 2030 RCP8.5            
```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH30_rcp85_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH30_rcp85_PB_01_ACCESS1-0"
  ) %>%
  dopvaplot(cc = TRUE)
```

```{r}
pvr_r %>%
  filter(
    yearid == "EG20",
    cscnid == "TH30_rcp85_PB_01_ACCESS1-0"
  ) %>%
  doccplot
```


# Only Access 1 RCP 4.5 CH and EG 20

```{r}
knitr::opts_chunk$set(fig.width=6, fig.height=4, echo = FALSE, message = FALSE)
```

```{r}
pvr_ra <- pvr_r %>% 
  filter(
    climate_model == "ACCESS1-0",
    rcp == "rcp45",
    yearid != "EG19"
  )

pvr_ra
```

## By Landscape 

### raw

```{r}
p_emp_peau_ls <- ggplot(pvr_ra)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = emp#,
      #fill = yearid#,
      #col = habitat
    )
  ) +
  geom_point(
    aes(
      x = emp,
      y = scn
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Expected minimum population",
    y = "Management scenario",
    #fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) +
  xlim(0, NA)

p_emp_peau_ls
```

```{r}
p_emp95_peau_ls <- ggplot(pvr_ra)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = emp_95#,
      #fill = yearid#,
      #col = habitat
    )
  ) +
  geom_point(
    aes(
      x = emp_95,
      y = scn
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Expected minimum population",
    y = "Management scenario",
    #fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) +
  xlim(0, NA)

p_emp95_peau_ls
```

```{r}
p_empmed_peau_ls <- ggplot(pvr_ra)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = emp_med,
      #fill = yearid#,
      #col = habitat
    )
  ) +
  geom_point(
    aes(
      x = emp_med,
      y = scn
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Median minimum population",
    y = "Management scenario",
    #fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) +
  xlim(0, NA)

p_empmed_peau_ls
```

```{r}
p_med_peau_ls <- ggplot(pvr_ra)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = med_pop,
      #fill = yearid#,
      #col = habitat
    )
  ) +
  geom_point(
    aes(
      x = med_pop,
      y = scn
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Median population",
    y = "Management scenario",
    #fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) +
  xlim(0, NA)

p_med_peau_ls
```

```{r}
p_pex_peau_ls <- ggplot(pvr_ra)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = prop_extant,
      #fill = yearid#,
      #col = habitat
    )
  ) +
  geom_point(
    aes(
      x = prop_extant,
      y = scn
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Probability of persistence",
    y = "Management scenario",
    #fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) +
  xlim(NA, 1)


p_pex_peau_ls
```

```{r}
p_tex_peau_ls <- ggplot(pvr_ra)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = mean_tt_ex#,
      #fill = yearid#,
      #col = habitat
    )
  ) +
  geom_point(
    aes(
      x = mean_tt_ex,
      y = scn
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Mean time to extinction\n(if extinct)",
    y = "Management scenario",
    #fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  ) +
  facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_tex_peau_ls
```

### delta

```{r}
p_demp_peau_ls <- ggplot(pvr_ra) +# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_emp#,
      #fill = yearid#,
      #col = habitat
    )
  ) +
  geom_point(
    aes(
      x = delta_emp,
      y = scn
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in expected minimum population from baseline\n(ongoing harvest)",
    y = "Management scenario",
    #fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_demp_peau_ls
```

```{r}
p_demp95_peau_ls <- ggplot(pvr_ra)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_emp_95#,
      #fill = yearid#,
      #col = habitat
    )
  ) +
  geom_point(
    aes(
      x = delta_emp_95,
      y = scn
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in expected minimum population from baseline\n(ongoing harvest)",
    y = "Management scenario",
    #fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  ) +
  facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_demp95_peau_ls
```

```{r}
p_dempmed_peau_ls <- ggplot(pvr_ra)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_emp_med#,
      #fill = yearid#,
      #col = habitat
    )
  ) +
  geom_point(
    aes(
      x = delta_emp_med,
      y = scn
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in median minimum population from baseline\n(ongoing harvest)",
    y = "Management scenario",
    #fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_dempmed_peau_ls
```

```{r}
p_dmed_peau_ls <- ggplot(pvr_ra)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_med_pop#,
      #fill = yearid#,
      #col = habitat
    )
  ) +
  geom_point(
    aes(
      x = delta_med_pop,
      y = scn
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in median population from baseline\n(ongoing harvest)",
    y = "Management scenario",
    #fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_dmed_peau_ls
```

```{r}
p_dpex_peau_ls <- ggplot(pvr_ra)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_prop_extant#,
      #fill = yearid#,
      #col = habitat
    )
  ) +
  geom_point(
    aes(
      x = delta_prop_extant,
      y = scn
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in probability of persistence from baseline\n(ongoing harvest)",
    y = "Management scenario",
    #fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_dpex_peau_ls
```

```{r}
p_dtex_peau_ls <- ggplot(pvr_ra)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_mean_tt_ex#,
      #fill = yearid#,
      #col = habitat
    )
  ) +
  geom_point(
    aes(
      x = delta_mean_tt_ex,
      y = scn
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in mean time to extinction (if extinct)\nfrom baseline (ongoing harvest)",
    y = "Management scenario",
    #fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_dtex_peau_ls
```

# East Gippsland comparison Only Access 1 RCP 4.5 CH and EG 20

```{r}
knitr::opts_chunk$set(fig.width=6, fig.height=4, echo = FALSE, message = FALSE)
```

```{r}
pvr_eg <- pvr_r %>% 
  filter(
    climate_model == "ACCESS1-0",
    rcp == "rcp45",
    landscape == "East Gippsland"
  )

pvr_eg
```

## By Landscape 

### raw

```{r}
p_emp_peau_ls <- ggplot(pvr_eg)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = emp,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d(begin = 0.5) +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Expected minimum population",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  #facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) +
  xlim(0, NA)

p_emp_peau_ls
```

```{r}
p_emp95_peau_ls <- ggplot(pvr_eg)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = emp_95,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d(begin = 0.5) +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Expected minimum population",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  #facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) +
  xlim(0, NA)

p_emp95_peau_ls
```

```{r}
p_empmed_peau_ls <- ggplot(pvr_eg)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = emp_med,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d(begin = 0.5) +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Median minimum population",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  #facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) +
  xlim(0, NA)

p_empmed_peau_ls
```

```{r}
p_med_peau_ls <- ggplot(pvr_eg)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = med_pop,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d(begin = 0.5) +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Median population",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  ) +
  #facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) +
  xlim(0, NA)

p_med_peau_ls
```

```{r}
p_pex_peau_ls <- ggplot(pvr_eg)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = prop_extant,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d(begin = 0.5) +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Probability of persistence",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  ) +
  #facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) +
  xlim(NA, 1)


p_pex_peau_ls
```

```{r}
p_tex_peau_ls <- ggplot(pvr_eg)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = mean_tt_ex,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d(begin = 0.5) +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Mean time to extinction\n(if extinct)",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  ) +
  #facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_tex_peau_ls
```

### delta

```{r}
p_demp_peau_ls <- ggplot(pvr_eg)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_emp,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d(begin = 0.5) +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in expected minimum population from baseline\n(ongoing harvest)",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  #facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_demp_peau_ls
```

```{r}
p_demp95_peau_ls <- ggplot(pvr_eg)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_emp_95,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d(begin = 0.5) +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in expected minimum population from baseline\n(ongoing harvest)",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  #facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_demp95_peau_ls
```

```{r}
p_dempmed_peau_ls <- ggplot(pvr_eg)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_emp_med,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d(begin = 0.5) +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in median minimum population from baseline\n(ongoing harvest)",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  #facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_dempmed_peau_ls
```

```{r}
p_dmed_peau_ls <- ggplot(pvr_eg)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_med_pop,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d(begin = 0.5) +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in median population from baseline\n(ongoing harvest)",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  #facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_dmed_peau_ls
```

```{r}
p_dpex_peau_ls <- ggplot(pvr_eg)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_prop_extant,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d(begin = 0.5) +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in probability of persistence from baseline\n(ongoing harvest)",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  #facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_dpex_peau_ls
```

```{r}
p_dtex_peau_ls <- ggplot(pvr_eg)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_mean_tt_ex,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d(begin = 0.5) +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in mean time to extinction (if extinct)\nfrom baseline (ongoing harvest)",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  #facet_grid(.~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_dtex_peau_ls
```







# All climate models
```{r}
knitr::opts_chunk$set(fig.width=6, fig.height=8, echo = FALSE, message = FALSE)
```

## By Landscape 

### raw

```{r}
p_emp_peau_ls <- ggplot(pvr_r)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = emp,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Expected minimum population",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(climate_model~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) +
  xlim(0, NA)

p_emp_peau_ls
```

```{r}
p_emp95_peau_ls <- ggplot(pvr_r)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = emp_95,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Expected minimum population",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(climate_model~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) +
  xlim(0, NA)

p_emp95_peau_ls
```

```{r}
p_empmed_peau_ls <- ggplot(pvr_r)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = emp_med,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Median minimum population",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(climate_model~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) +
  xlim(0, NA)

p_empmed_peau_ls
```

```{r}
p_med_peau_ls <- ggplot(pvr_r)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = med_pop,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Median population",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(climate_model~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) +
  xlim(0, NA)

p_med_peau_ls
```

```{r}
p_pex_peau_ls <- ggplot(pvr_r)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = prop_extant,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Probability of persistence",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(climate_model~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) +
  xlim(NA, 1)


p_pex_peau_ls
```

```{r}
p_tex_peau_ls <- ggplot(pvr_r)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_boxplot(
    aes(
      y = scn,
      x = mean_tt_ex,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Mean time to extinction\n(if extinct)",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(climate_model~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_tex_peau_ls
```

### delta

```{r}
p_demp_peau_ls <- ggplot(pvr_r)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_emp,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in expected minimum population from baseline\n(ongoing harvest)",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(climate_model~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_demp_peau_ls
```

```{r}
p_demp95_peau_ls <- ggplot(pvr_r)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_emp_95,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in expected minimum population from baseline\n(ongoing harvest)",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(climate_model~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_demp95_peau_ls
```

```{r}
p_dempmed_peau_ls <- ggplot(pvr_r)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_emp_med,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in median minimum population from baseline\n(ongoing harvest)",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(climate_model~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_dempmed_peau_ls
```

```{r}
p_dmed_peau_ls <- ggplot(pvr_r)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_med_pop,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in median population from baseline\n(ongoing harvest)",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(climate_model~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_dmed_peau_ls
```

```{r}
p_dpex_peau_ls <- ggplot(pvr_r)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_prop_extant,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in probability of persistence from baseline\n(ongoing harvest)",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(climate_model~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_dpex_peau_ls
```

```{r}
p_dtex_peau_ls <- ggplot(pvr_r)+# %>% filter(climate_model == "ACCESS1-0", habitat == "projected")) +
  geom_vline(xintercept = 0) +
  geom_boxplot(
    aes(
      y = scn,
      x = delta_mean_tt_ex,
      fill = yearid#,
      #col = habitat
    )
  ) +
  scale_fill_viridis_d() +
  scale_colour_manual(values = c("grey10", "grey40")) +
  labs(
    x = "Change in mean time to extinction (if extinct)\nfrom baseline (ongoing harvest)",
    y = "Management scenario",
    fill = "Landscape\n& year",
    title = spti#,
    #col = "Habitat\nmodel"
  )+
  facet_grid(climate_model~yearid, scales = "free_x") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 270)) 

p_dtex_peau_ls
```


