---
title: "Habitat model data"
output: html_notebook
---

## Prelims

### Packages
```{r packages}
library(raster)
library(rgdal)
library(rgeos)
library(dismo)
library(viridis)
library(foreach)
library(maptools)
```

### Functions
```{r functions}
source("R/functions.R")
```

## Spatial Data

### Extent area
Extent layer
```{r ch_rst}
ch_rst <- raster("data/grids/VIC_GDA9455_GRID_CENTRALHIGHLANDS_100.tif")
ch_rst
```

Gather spatial information from mask layer
```{r ch info}
(ch_res <- res(ch_rst))
(ch_extent <- extent(ch_rst))
(ch_proj <- ch_rst@crs)
```

Create clipping mask that is X kilometers larger than extent in both directions
```{r clipping mask}
(km_offset <- 10)
(ch_extent_offset <- extent(ch_rst) + km_offset*(1000))
```

Create window for focal operations
*Why this radius?*
```{r focal window}
buffer_radius <- 564
window <- focalWeight(raster(ncols=11, nrows=11, xmn=0),
                      buffer_radius,
                      type = 'circle')
```

### Proportion wet forest
Spatial layer
*This layer is presence of forest which is then processed into proportion later?*
```{r NVIS}
system(paste0("gdalwarp -overwrite -tr 100 100 -s_srs '+proj=aea +lat_1=-18 +lat_2=-36 +lat_0=0 +lon_0=132 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs' -t_srs '+proj=utm +zone=55 +south +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs' -te ", paste(ch_extent_offset[1], ch_extent_offset[3], ch_extent_offset[2], ch_extent_offset[4]), " ", getwd(), "/data/grids/raw/GRID_NVIS5_1_AUST_EXT_MVS/aus5_1e_mvs/w001000.adf ", getwd(), "/data/grids/raw/NVIS_GDA9455.tif")) # reproject to project coordinate system
NVIS <- raster("data/grids/raw/NVIS_GDA9455.tif")
NVIS <- calc(NVIS, fun = function(x) {x[x != 3] <- NA; return(x) }) # only retain wet sclerophyll Eucalyptus forest
NVIS[!is.na(NVIS)] <- 1
NVIS
```

Process
```{r PROP_WET_FOREST}
PROP_WET_FOREST <- focal(NVIS, window, na.rm = TRUE) 
PROP_WET_FOREST[is.na(PROP_WET_FOREST)] <- 0
PROP_WET_FOREST <- crop(PROP_WET_FOREST, ch_extent)
PROP_WET_FOREST
```
*Why do NAs become 0?*


### Proportion old growth forest
```{r OG100}
OG100 <- readOGR("data/shapefiles", "OG100", stringsAsFactors = FALSE)
OG100 <- subset(OG100, X_OGDESC == "Old Growth Forest")
OG100 <- spTransform(OG100, ch_proj) # reproject to project coordinate system
OG100 <- crop(OG100, ch_extent_offset)
OG100r <- rasterize(OG100, raster(res = ch_res, ext = ch_extent_offset, crs = ch_proj), 1)

writeRaster(OG100r, file = "data/grids/raw/OLDGROWTH_GDA9455.tif", overwrite = TRUE)
system(paste0("gdal_proximity.py ", getwd(), "/data/grids/raw/OLDGROWTH_GDA9455.tif ", getwd(), "/data/grids/raw/VIC_GDA9455_DIST_OLDGROWTH.tif -values 1 -distunits GEO")) # reproject to project coordinate system
```


```{r PROP_OLD_GROWTH}
PROP_OLD_GROWTH <- focal(OG100r, window, na.rm = TRUE) 
PROP_OLD_GROWTH[is.na(PROP_OLD_GROWTH)] <- 0
PROP_OLD_GROWTH <- crop(PROP_OLD_GROWTH, ch_extent)
PROP_OLD_GROWTH
```

### Proportion Tall Forest
```{r AUSCOVER}
system(paste0("gdalwarp -overwrite -tr 100 100 -s_srs '+proj=aea +lat_1=-18 +lat_2=-36 +lat_0=0 +lon_0=132 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs' -t_srs '+proj=utm +zone=55 +south +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs' -te ", paste(ch_extent_offset[1], ch_extent_offset[3], ch_extent_offset[2], ch_extent_offset[4]), " ", getwd(), "/data/grids/raw/alpsbk_aust_y2009_sf1a2.tif ", getwd(), "/data/grids/raw/AUSCOVER_GDA9455.tif")) # reproject to project coordinate system
AUSCOVER <- raster("data/grids/raw/AUSCOVER_GDA9455.tif")
AUSCOVER <- calc(AUSCOVER, fun = function(x) {x[x != 44 & x != 54 & x != 55 & x != 64] <- NA; return(x) }) # only retain tall forest (>30m)
AUSCOVER[!is.na(AUSCOVER)] <- 1
AUSCOVER
```
*How do these calculations work? You set NAs to be forest <30 m, then this is processed in focal area, then anything still NA is zero?*
```{r PROP_TALL_FOREST}
PROP_TALL_FOREST <- focal(AUSCOVER, window, na.rm = TRUE) 
PROP_TALL_FOREST[is.na(PROP_TALL_FOREST)] <- 0
PROP_TALL_FOREST <- crop(PROP_TALL_FOREST, ch_extent)
PROP_TALL_FOREST
```

### Combine Spatial Variables
```{r gg_env_vars}
gg_env_vars <- stack(PROP_WET_FOREST, PROP_OLD_GROWTH, PROP_TALL_FOREST) #Combine all maps to single stack
names(gg_env_vars) <- c("PROP_WF", "PROP_OG", "PROP_TF")
gg_env_vars
```
Write out covariates to binary file *why not GeoTiff etc?*
```{r save gg_env_vars}
save(gg_env_vars, file="data/gg_env_vars")
```

### RFA boundary
```{r rfa_boundary}
rfa_boundary <- readOGR(dsn="data/shapefiles", layer="RFA")
rfa_boundary <- rfa_boundary[rfa_boundary@data$NAME == "CENTRAL HIGHLANDS", ]
rfa_boundary <- spTransform(rfa_boundary, ch_proj)
rfa_boundary
```

## GG points

### GG points data
```{r GG_POINTS}
gg_pres_abs <- read.csv(file="data/tabular/vicAtlasGGpresabs.csv")

coords <- data.frame(X = gg_pres_abs$LongitudeGDA94,
                     Y = gg_pres_abs$LatitudeGDA94)
coordinates(coords) <- c("X", "Y")
proj4string(coords) <- CRS("+init=epsg:4283") # GDA94
GG_POINTS <- data.frame("PA" = gg_pres_abs[, 1], spTransform(coords, ch_proj)@coords)
GG_POINTS
```

```{r plot gg points rfa}
plot(rfa_boundary)
points(GG_POINTS[GG_POINTS$PA == 0, 2:3], col = "darkred")
points(GG_POINTS[GG_POINTS$PA == 1, 2:3], pch = 2)
```

### Process GG points and env data
 Sample covariate values - be sure to use select correct data
```{r cov_sample}
(cov_sample <- as.data.frame(extract(gg_env_vars, GG_POINTS[, 2:3])))
```


Create modelling dataset - be sure to use select correct data
```{r gg_model_data}
(gg_model_data <- cbind("PA" = GG_POINTS[, 1], cov_sample))
```
Check for NA values and omit accordingly:
```{r check NA}
(sum(is.na(gg_model_data)))
```
```{r omit NA}
(gg_model_data <- na.omit(gg_model_data))
```
Review pairwise correlation of covariates:
```{r cor gg_model_dat}
(cor(gg_model_data[, 2:4]))
```
Review covariate data types
```{r str gg_model_dat}
str(gg_model_data)
```
Review data ranges
```{r ranges gg_model_data}
apply(gg_model_data[, 2:4], 2, range)
```

Split the data into training and testing data
```{r split gg_model data}
set.seed(123)
gg_sample <- sample(nrow(gg_model_data), round(0.75 * nrow(gg_model_data))) # the row indexes of our 75% sample
gg_model_data_75 <- gg_model_data[gg_sample, ] # 75% of the data used to train the model
gg_model_data_25 <- gg_model_data[-gg_sample, ] # 25% of the data used to test the model
```

Write the modelling data out to csv files and as an R object
```{r write gg_model data}
write.csv(gg_model_data, file = "data/gg_model_data.csv")
write.csv(gg_model_data_25, file = "data/gg_model_data_25.csv")
write.csv(gg_model_data_75, file = "data/gg_model_data_75.csv")
save("gg_model_data", "gg_model_data_25", "gg_model_data_75", file = "data/gg_model_datasets")
```

