---
title: "R Notebook"
output: html_notebook
---


```{r}
# matrix(
#   data = c(
#     , , ,
#     , , ,
#     , , 
#   ),
#   nrow = 3,
#   ncol = 3,
#   byrow = TRUE,
#   dimnames = list(
#     c('Newborn','Juvenile','Adult'),
#     c('Newborn','Juvenile','Adult')
#   )
# )
```


## Leadbeater's possum
```{r}
tm_gyle <- matrix(
  data = c(
   0.00, 0.00, 0.80,
   0.50, 0.00, 0.00,
   0.00, 0.60, 0.88
  ),
  nrow = 3,
  ncol = 3,
  byrow = TRUE,
  dimnames = list(
    c('Newborn','Juvenile','Adult'),
    c('Newborn','Juvenile','Adult')
  )
)

tm_gyle

rmax(tm_gyle)
```


## Greater Glider
```{r}
tm_pevo <- matrix(
  data = c(
   0.00, 0.00, 0.50,
   0.50, 0.00, 0.00,
   0.00, 0.85, 0.90
  ),
  nrow = 3,
  ncol = 3,
  byrow = TRUE,
  dimnames = list(
    c('Newborn','Juvenile','Adult'),
    c('Newborn','Juvenile','Adult')
  )
)

tm_pevo

rmax(tm_pevo)
```


## Yellow-bellied glider
Direct from comadre database. Possibly naiive specification - Mick commented that prob is pre-breeding but if birth rate is equal all are 
```{r}
tm_peau <- matrix(
  data = c(
    0.0, 0.0, 0.5,
    0.7, 0.0, 0.0,
    0.0, 0.6, 0.8
  ),
  nrow = 3,
  ncol = 3,
  byrow = TRUE,
  dimnames = list(
    c('Newborn','Juvenile','Adult'),
    c('Newborn','Juvenile','Adult')
  )
)

tm_peau

rmax(tm_peau)
```

## White-footed dunnart
```{r}
tm_smle <- matrix(
  data = c(
    0.00, 4.20,
    0.29, 0.05
  ),
  nrow = 2,
  ncol = 2,
  byrow = TRUE,
  dimnames = list(
    c('Newborn', 'Adult'),
    c('Newborn', 'Adult')
  )
)

tm_smle

rmax(tm_smle)
```

## Lace Monitor
```{r}
vava_j_surv <- reptile_juv_survival(
  a = 4,
  Sa = 0.93,
  n = 1,
  c = 7.8
)
vava_j_surv
```

```{r}
tm_vava <- matrix(
  data = c(
    0.00, 0.00, 0.00, 2.69,
    0.37, 0.00, 0.00, 0.00, 
    0.00, 0.37, 0.00, 0.00,
    0.00, 0.00, 0.37, 0.93
  ),
  nrow = 4,
  ncol = 4,
  byrow = TRUE,
  dimnames = list(
    c('Hatchling','Juvenile', "Sub-adult",'Adult'),
    c('Hatchling','Juvenile', "Sub-adult",'Adult')
  )
)

tm_vava

rmax(tm_vava)
```
## Sooty Owl
Based on survival estimates for juv Powerful Owl, clutch size of "usually 1" but give 1 in 10 chance of 2, and proportion of 0.69 first year animals breeding (from Barn Owl)
```{r}
tm_tyte <- matrix(
  data = c(
           0.00, 0.00, 0.55,
    0.31 * 0.67, 0.00, 0.00,
    0.69 * 0.67, 0.67, 0.74 
  ),
  nrow = 3,
  ncol = 3,
  byrow = TRUE,
  dimnames = list(
    c('Newborn','Sub-adult','Adult'),
    c('Newborn','Sub-adult','Adult')
  )
)

tm_tyte

rmax(tm_tyte)
```



## Long-footed potoroo