---
title: "Are our pre- and post-breeding census matrix models consistent and therefore possibly correctly specified or are Gerry and Casey dimwits with no hope of ever grasping anything?"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
library(dplyr)
```

Pre-breeding census matrix

|     |Juv    |Adult              |
|-----|-------|-------------------|
|  Juv|-      |NewbSurv * AdultFec|
|Adult|JuvSurv|AdultSurv          |
```{r}
premat <- matrix(data = c(0.00, 0.50*0.50,
                          0.85,      0.85),
                 nrow = 2,
                 byrow = TRUE)


premat
```
Postbreeding census matrix

|     |Newb    | Juv              | Adult              |
|-----|--------|------------------|--------------------|
|Newb |-       |JuvSurv * AdultFec|AdultSurv * AdultFec|
|Juv  |NewbSurv|-                 |-                   |
|Adult|-       |JuvSurv           |AdultSurv           |
```{r}
postmat <- matrix(data = c(0.00, 0.85*0.50, 0.85*0.50,
                           0.50,      0.00,      0.00,
                           0.00,      0.85,      0.85),
                  nrow = 3,
                  byrow = TRUE)

postmat
```

Take a population of 100 adults immediately before breeding at time t0

```{r}
prepop0 <- matrix(c(0,
                    100),
                  nrow = 2)

prepop0
```

The same population immediately after breeding but still at time t0
```{r}
postpop0 <- matrix(c(100*0.5,
                     0,
                     100),
                   nrow = 3)

postpop0
```


Now after the first timestep our prebreeding population would be
```{r}
prepop1 <- premat %*% prepop0 # note matrix multiplicaiton symbol %*%

prepop1
```


> *NB: initial population needs to be a vertical matrix, not a vector or the numbers don't work out correctly, E.g.:*
```{r}
premat* c(0, 100)
```
> *This suggests that there are 170 animals from a population of 100 with a fecundity of 0.25 - clearly rubbish.*

> *Alternatively you need to transpose the original matrix*
```{r}
t(premat) * c(0, 100)
```
> *So I think it's easier for me to work in the same way I would write it, with a vertical matrix, but whatever you want to do be careful that everything agrees, anyhow. But back to the main point.*

So our pre-breeding population immediately *after* breeding at time t1 would be
```{r}
prepop1_post <- matrix(c(85*0.5,
                       25,
                       85),
                       nrow = 3) %>%
  round

prepop1_post
```

Meanwhile our postbreeding population at 
```{r}
postpop1 <- postmat %*% postpop0 %>%
  round

postpop1
```
 **Yay! It's consistent!**
 
 How about into t2?
```{r}
prepop2 <- premat %*% prepop1 %>%
  round

prepop2
```
 
Which after breeding at t2 becomes
```{r}
prepop2_post <- matrix(c(94 * 0.5,
                         21,
                         94),
                       nrow = 3)

prepop2_post
```

And our post-breeding population at t2 is
```{r}
postpop2 <- postmat %*% postpop1 %>%
  round

postpop2
```

# **FUCK YEAH**
We're not complete idiots.